### 2021-05-12 seminar.tex
Initial commit

\documentclass[	runningheads,
				%deutsch, % Tell llncs that the keywords should be in german
				%german,  % Needed for the \ifgerman-command
				a4paper]{llncs}

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}

% Support for special characters like "Umlaute"
\usepackage[utf8]{inputenc}

\ifgerman{
	\usepackage[ngerman]{babel}
	\usepackage{ngerman}
	\usepackage{bibgerm}        % German symbols in BibTeX
}{
	\usepackage[english]{babel}
}

%*********************************************************************%
% META                                                                %
%*********************************************************************%
\ifgerman{
	\newcommand{\university}{Universität des Saarlandes}
	\newcommand{\school}{Saarland Informatics Campus}
}{
\newcommand{\university}{Saarland University}
\newcommand{\school}{Saarland Informatics Campus}
}
\ifgerman{ 
	\newcommand{\thetitle}{Seminar: Title of the Seminar}
	\newcommand{\shorttitle}{Seminar: Title of the Semianr}
	\newcommand{\thedate}{18. Oktober}
}{
\newcommand{\thetitle}{Seminar: Title of the Seminar}
\newcommand{\shorttitle}{Seminar: Title of the Seminar}
\newcommand{\thedate}{April 15}
\newcommand{\thegermandate}{15. April}
}

\newcommand{\theforename}{Max}
\newcommand{\thesurname}{Mustermann}

% Advisors
\ifgerman{
	\newcommand{\advisor}{Betreuer}
	}{
	\newcommand{\advisor}{Advisors}
	}
	\newcommand{\advisors}{Prof. Sven Apel, \\ \$ADVISOR}

% Title for the seminar
\ifgerman{
	\newcommand{\theseminartitle}{Titel des Arbeit}
}{
	\newcommand{\theseminartitle}{Title of the paper}
}

%*********************************************************************%
% THE DOCUMENT                                                        %
%*********************************************************************%

\begin{document}
	%*********************************************************************%
	% TITLE                                                               %
	%*********************************************************************%

	% Arabic page numbering
	\mainmatter

	% Title including a subtitle for the name of the seminar
	\title{\theseminartitle \\ \small \thetitle}

	% (Optional) In the case that the initial title is too long, the short title will be used
	%\titlerunning{Hauptseminar: Human and Social Factors in Software Engineering}

	\author{\theforename\ \thesurname \small \\ \ \\ \advisor : \ \advisors}

	% (Optional) This will appear near the page number
	\authorrunning{\shorttitle}

	\institute{\school ,\\ \university}

	\maketitle

	%*********************************************************************%
	% CONTENT                                                             %
	%*********************************************************************%

	% Introduction
	\ifgerman{\section{Einführung}}{\section{Introduction}}

	You are strongly encouraged to use \LaTeXe{} for the
preparation of your camera-ready manuscript together with the
corresponding Springer class file \verb+llncs.cls+. Only if you use
\LaTeXe{} can hyperlinks be generated in the online version
of your manuscript.

The \LaTeX{} source of this instruction file for \LaTeX{} users may be
used as a template. This is
located in the ``authors'' subdirectory in
\url{ftp://ftp.springer.de/pub/tex/latex/llncs/latex2e/instruct/} and
entitled \texttt{typeinst.tex}. There is a separate package for Word 
users. Kindly send the final and checked source
and PDF files of your paper to the Contact Volume Editor. This is
usually one of the organizers of the conference. You should make sure
that the \LaTeX{} and the PDF files are identical and correct and that
only one version of your paper is sent. It is not possible to update
files at a later stage. Please note that we do not need the printed
paper.

We would like to draw your attention to the fact that it is not possible
to modify a paper in any way, once it has been published. This applies
to both the printed book and the online version of the publication.
Every detail, including the order of the names of the authors, should
be checked before the paper is sent to the Volume Editors.

\subsection{Checking the PDF File}

Kindly assure that the Contact Volume Editor is given the name and email
address of the contact author for your paper. The Contact Volume Editor
uses these details to compile a list for our production department at
SPS in India. Once the files have been worked upon, SPS sends a copy of
the final pdf of each paper to its contact author. The contact author is
asked to check through the final pdf to make sure that no errors have
crept in during the transfer or preparation of the files. This should
not be seen as an opportunity to update or copyedit the papers, which is
not possible due to time constraints. Only errors introduced during the
preparation of the files will be corrected.

This round of checking takes place about two weeks after the files have
been sent to the Editorial by the Contact Volume Editor, i.e., roughly
seven weeks before the start of the conference for conference
proceedings, or seven weeks before the volume leaves the printer's, for
post-proceedings. If SPS does not receive a reply from a particular
contact author, within the timeframe given, then it is presumed that the
author has found no errors in the paper. The tight publication schedule
of LNCS does not allow SPS to send reminders or search for alternative
email addresses on the Internet.

In some cases, it is the Contact Volume Editor that checks all the final
pdfs. In such cases, the authors are not involved in the checking phase.

\subsection{Additional Information Required by the Volume Editor}

If you have more than one surname, please make sure that the Volume Editor
knows how you are to be listed in the author index.

\subsection{Copyright Forms}

The copyright form may be downloaded from the ``For Authors"
(Information for LNCS Authors) section of the LNCS Website:
\texttt{www.springer.com/lncs}. Please send your signed copyright form
to the Contact Volume Editor, either as a scanned pdf or by fax or by
courier. One author may sign on behalf of all of the other authors of a
particular paper. Digital signatures are acceptable.

\section{Paper Preparation}

Springer provides you with a complete integrated \LaTeX{} document class
(\texttt{llncs.cls}) for multi-author books such as those in the LNCS
series. Papers not complying with the LNCS style will be reformatted.
This can lead to an increase in the overall number of pages. We would
therefore urge you not to squash your paper.

Please always cancel any superfluous definitions that are
not actually used in your text. If you do not, these may conflict with
the definitions of the macro package, causing changes in the structure
of the text and leading to numerous mistakes in the proofs.

If you wonder what \LaTeX{} is and where it can be obtained, see the
``\textit{LaTeX project site}'' (\url{http://www.latex-project.org})
and especially the webpage ``\textit{How to get it}''
(\url{http://www.latex-project.org/ftp.html}) respectively.

When you use \LaTeX\ together with our document class file,
\texttt{llncs.cls},
your text is typeset automatically in Computer Modern Roman (CM) fonts.
Please do
\emph{not} change the preset fonts. If you have to use fonts other
than the preset fonts, kindly submit these with your files.

Please use the commands \verb+\label+ and \verb+\ref+ for
cross-references and the commands \verb+\bibitem+ and \verb+\cite+ for
references to the bibliography, to enable us to create hyperlinks at
these places.

For preparing your figures electronically and integrating them into
your source file we recommend using the standard \LaTeX{} \verb+graphics+ or
\verb+graphicx+ package. These provide the \verb+\includegraphics+ command.
In general, please refrain from using the \verb+\special+ command.

Remember to submit any further style files and
fonts you have used together with your source files.

\subsubsection{Headings.}

Headings should be capitalized
(i.e., nouns, verbs, and all other words
except articles, prepositions, and conjunctions should be set with an
initial capital) and should,
with the exception of the title, be aligned to the left.
Words joined by a hyphen are subject to a special rule. If the first
word can stand alone, the second word should be capitalized.

Here are some examples of headings: ``Criteria to Disprove
Context-Freeness of Collage Language", ``On Correcting the Intrusion of
Tracing Non-deterministic Programs by Software", ``A User-Friendly and
Extendable Data Distribution System", ``Multi-flip Networks:
Parallelizing GenSAT", ``Self-determinations of Man".

\subsubsection{Lemmas, Propositions, and Theorems.}

The numbers accorded to lemmas, propositions, and theorems, etc. should
appear in consecutive order, starting with Lemma 1, and not, for
example, with Lemma 11.

	\ifgerman{\section{Zusammenfassung}}{\section{Conclusion}}

	%*********************************************************************%
	% APPENDIX                                                            %
	%*********************************************************************%

	\appendix
	\ifgerman{\section{Anhang}}{\section{Appendix}}
	% Insert the appendix here. You can alternatively include files via: \include{pathToFile}

	%*********************************************************************%
	% LITERATURE                                                          %
	%*********************************************************************%
	% As a recommendation JabRef might be a usefull tool for this section. Use myRefs.bib therefore
	\phantomsection
	\bibliographystyle{splncs03}
	\bibliography{literature}

\end{document}

### 2021-06-27 code/visualization/main.py
* Added benchmark results * Added python for visualization

@@ -1,0 +1,36 @@
+import csv
+import os
+
+import matplotlib.pyplot as plt
+
+
+def plot_release_data():
+    release_res_dir = "../../results/releases_benchmark/"
+    labels = []
+    compression_speed = []
+    decompression_speed = []
+
+    for filename in os.listdir(release_res_dir):
+        with open(os.path.join(release_res_dir, filename)) as res_file:
+            labels.append(filename.strip(".res"))
+            reader = csv.reader(res_file)
+            next(reader)
+            next(reader)
+            line = next(reader)
+            compression_speed.append(float(line[1]))
+            decompression_speed.append(float(line[2]))
+
+    plt.plot(labels, compression_speed)
+    plt.ylabel('MB/s')
+    plt.xlabel("Version")
+    plt.ylim([0, 600.0])
+    plt.xticks(rotation=90)
+    plt.tight_layout()
+    plt.savefig("compression_plot.png")
+
+
+# Press the green button in the gutter to run the script.
+if __name__ == '__main__':
+    plot_release_data()
+
+# See PyCharm help at https://www.jetbrains.com/help/pycharm/

### 2021-08-23 tex/experiment_idea.tex
Restructured project to have tex and scripts in one git

\documentclass[	runningheads,
				%deutsch, % Tell llncs that the keywords should be in german
				%german,  % Needed for the \ifgerman-command
				a4paper]{llncs}

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}

% Support for special characters like "Umlaute"
\usepackage[utf8]{inputenc}

\ifgerman{
	\usepackage[ngerman]{babel}
	\usepackage{ngerman}
	\usepackage{bibgerm}        % German symbols in BibTeX
}{
	\usepackage[english]{babel}
}

%*********************************************************************%
% META                                                                %
%*********************************************************************%
\ifgerman{
	\newcommand{\university}{Universität des Saarlandes}
	\newcommand{\school}{Saarland Informatics Campus}
}{
\newcommand{\university}{Saarland University}
\newcommand{\school}{Saarland Informatics Campus}
}
\ifgerman{ 
	\newcommand{\thetitle}{Seminar: Title of the Seminar}
	\newcommand{\shorttitle}{Seminar: Title of the Semianr}
	\newcommand{\thedate}{18. Oktober}
}{
\newcommand{\thetitle}{Seminar: Systems Benchmarking}
\newcommand{\shorttitle}{Seminar: Systems Benchmarking}
\newcommand{\thedate}{April 15}
\newcommand{\thegermandate}{15. April}
}

\newcommand{\theforename}{Lukas}
\newcommand{\thesurname}{Abelt}

% Advisors
\ifgerman{
	\newcommand{\advisor}{Betreuer}
	}{
	\newcommand{\advisor}{Advisors}
	}
	\newcommand{\advisors}{Prof. Sven Apel, \\ Christian Hechtl}

% Title for the seminar
\ifgerman{
	\newcommand{\theseminartitle}{Titel des Arbeit}
}{
	\newcommand{\theseminartitle}{"Performance Measurements Before Releases vs. Each Commits" -- Experiment Idea}
}

%*********************************************************************%
% THE DOCUMENT                                                        %
%*********************************************************************%

\begin{document}
	%*********************************************************************%
	% TITLE                                                               %
	%*********************************************************************%

	% Arabic page numbering
	\mainmatter

	% Title including a subtitle for the name of the seminar
	\title{\theseminartitle \\ \small \thetitle}

	% (Optional) In the case that the initial title is too long, the short title will be used
	%\titlerunning{Hauptseminar: Human and Social Factors in Software Engineering}

	\author{\theforename\ \thesurname \small \\ \ \\ \advisor : \ \advisors}

	% (Optional) This will appear near the page number
	\authorrunning{\shorttitle}

	\institute{\school ,\\ \university}

	\maketitle

	%*********************************************************************%
	% CONTENT                                                             %
	%*********************************************************************%

	% Introduction
	\ifgerman{\section{Einführung}}{\section{General}}
	This document will briefly outline the experiment idea for the topic "Performance Measurements Before Releases vs. Each Commits" in the seminar "Systems Benchmarking". The goal of this experiment and the corresponding paper is to showcase, how continous performance measurements throughout the whole development process can be used to detect and fix performance regressions at a very early stage.

	To achieve this, the experiment will first analyze the performance of public releases an open-source project to find a performance regression between two releases. Then, a performance measurement will be done for every commit between these two releases. We will use the data aquired by these performance measurements to demonstrate how or if various change detection measurements could havedetected this regression early on.

\section{Experiment Setup}

For my experiment I will use the open-source compression library \texttt{lz4}\footnote{\url{https://github.com/lz4/lz4}} as it has a active commit and release history. For the performance measurement itself we will use the latest version of the open-source project \texttt{lzbench}\footnote{https://github.com/inikep/lzbench}. Lzbench is an in-memory compression benchmarking tool that is originally designed to compare different compression algorithms. However for our case we will use it to simply only measure \texttt{lz4} at different releases/commits. For this case we will disable all other compression algorithms that \texttt{lzbench} supports at compile-time. First preliminary tests have shown that \texttt{lzbench} can easily use a different version of \texttt{lz4} than the shipped one by simply replacing the corresponding source files.

For the compression itself we will use the Silesia Data Corpus\footnote{http://sun.aei.polsl.pl/~sdeor/index.php?page=silesia}. The Sileasia Corpus combines a variety of different data in order to create a diverse dataset for compression measurements.

After identifying a performance regression between two releases we will collect data for the commits between these releases. To analyze the data collected for these commits we will compare the two following methods:
\begin{itemize}
	\item Comparing based on a static threshhold to the last commit/release
	\item Using Change Point Detection (Specifically E-Divisive Means)\footnote{As described in \url{https://dl.acm.org/doi/pdf/10.1145/3358960.3375791}}
\end{itemize}

For the change point detection we will use the implementation provided by MongoDB\footnote{https://github.com/mongodb/signal-processing-algorithms}. Since we will also store the raw performance data as returned by \texttt{lzbench} it is also possible to add further methods later on to get a better overview of different methods.

\section{Challenges and possible risks}
In this section I will briefly outline challenges, risks that might arise during the experiment and also outline possible solutions to them.

\subsection{Detecting regression between releases}
\subsubsection{Defining a regression threshhold}
One of the main challenges will be to define a threshhold for a performance regression between commits. As a first starter we will work with a static threshhold of 10\% as compared to the previous release. However if this value seems to many/less releases we might need to change the threshhold or overthink out strategy overall.

\subsubsection{No regression detected}
It might happen that we will detect no noticable performance changes whatsoever between the individual releases. One likely reason for this might be that the actual performance regressions happened while testing the release and where therefore fixed in the actual release.

One solution to this might be to select some commit for measurement before the release commit to benchmark on. However this would require a lot of manual triaging to select the "correct" commit based on e.g. the commit or issue history of the project.

Then still it could happen that with that strategy we do not detect any performance regressions (or improvements) that we can use as a guideline where to perform our finer measurement. In that case we could:
\begin{itemize}
	\item Select an arbitrary release range for our finer analysis -- However this itself bears the risk that we do not detect any change points in this range
	\item Select a release range based on issues submitted on the GitHub page that indicate that there at least was some performance regression during this period
	\item Select another project for our experiment
\end{itemize}

\subsection{Measuring individual commits}

\subsubsection{Commits that won't build}
If we measure all commits between two releases it is very likely that not all commits will be able to compile. We can easily take this into account by simply skipping these commits and not perform any measurements if we detect a failure during build.

\subsubsection{Number of commits}
Even when restricting us to the duration between two releases it might still happen that we end up with a lot of commits we need to benchmark individually. Depending how long one benchmark takes this could easily take too much time to finish in a reasonable time frame. Additionally we have to remember that also others might want to use the cluster environment for their experiments, so we should not clog it with hundreds of our jobs.

One possible measure to counteract this is to not measure each individual commit but squash them based on some criterion, e.g. only measuring one commit per day. In practice we will have to take a close look how long an individual performance measurement (including build etc.) takes so that we can esitmate how long our measurements would take in total.

\section{Possible Extensions}
There are a few possible extensions that could be appended to this experiment idea if time allows it:
\begin{itemize}
	\item Using the data collected by individual commits to show how individual commits can be compared effectively\footnote{As shown in \url{https://arxiv.org/pdf/2101.10231.pdf}}
	\item Extend the regression detection method
	\item Evaluate the impact on sustainability
\end{itemize}

	%*********************************************************************%
	% APPENDIX                                                            %
	%*********************************************************************%

	% Insert the appendix here. You can alternatively include files via: \include{pathToFile}

	%*********************************************************************%
	% LITERATURE                                                          %
	%*********************************************************************%
	% As a recommendation JabRef might be a usefull tool for this section. Use myRefs.bib therefore

\end{document}

### 2021-08-23 scripts/benchmark_releases.sh

@@ -1,0 +1,17 @@
+#!/bin/bash
+#SBATCH --job-name=labelt-lz4-release-benchmarks
+#SBATCH --exclusive
+#SBATCH --partition=seminar
+#SBATCH --constraint=kine
+#SBATCH --array=0-12
+#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4releases/release_benchmark_%A_%a.out
+#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4releases/release_benchmark_%A_%a.err
+
+USER=abeltluk
+USER_BASE_DIR=/scratch/$USER
+RELEASES_FILE=$USER_BASE_DIR/lz4releases
+
+RELEASES_LIST=($(<$RELEASES_FILE))
+RELEASE=${RELEASES_LIST[${SLURM_ARRAY_TASK_ID}]}
+
+srun ./run_benchmark.sh $RELEASE

### 2021-08-23 scripts/run_benchmark.sh

@@ -1,0 +1,48 @@
+#!/bin/bash
+
+# This bash file builds and benchmarks lz4 against a specific commit
+
+USER=abeltluk
+USER_BASE_DIR=/scratch/$USER
+LZBENCH_DIR=$USER_BASE_DIR/lzbench
+LZ4_DIR=$USER_BASE_DIR/lz4
+SILESIA_DIR=$USER_BASE_DIR/silesia
+
+RELEASE=$1
+
+REL_BENCH_BASE_DIR=$USER_BASE_DIR/commit_benchmark
+WORKING_DIR=$REL_BENCH_BASE_DIR/build/$RELEASE
+
+RESULT_FILE=$REL_BENCH_BASE_DIR/results/$RELEASE.res
+TIMINGS_FILE=$REL_BENCH_BASE_DIR/results/$RELEASE.timings
+
+# Setup environment
+mkdir $WORKING_DIR
+cd $WORKING_DIR
+
+# Copy LZBench and LZ4 from base
+cp -r $LZBENCH_DIR .
+cp -r $LZ4_DIR .
+
+# Copy siselia corpus
+cp -r $SILESIA_DIR .
+
+# Checkout correct version of lz4:
+cd ./lz4
+git checkout $RELEASE
+
+# Overwrite lz4 files of lzbench
+cd $WORKING_DIR
+cp -r ./lz4/lib/* ./lzbench/lz4
+
+# Build lzbench with new version
+cd ./lzbench
+make
+
+cd $WORKING_DIR
+# Run lzbench TODO
+./lzbench/lzbench -elz4 -i10,10 -j -r -o4 -v silesia > $RESULT_FILE
+
+# Cleanup
+cd $USER_BASE_DIR
+rm -rf $WORKING_DIR

### 2021-08-23 scripts/benchmark_commits.sh
Slightly adapted scripts to run

@@ -13,6 +13,7 @@ USER_BASE_DIR=/scratch/$USER
 RELEASES_FILE=$USER_BASE_DIR/lz4commits
 
 RELEASES_LIST=($(<$RELEASES_FILE))
+BENCH_BASE_DIR=$USER_BASE_DIR/commit_benchmark
 
 PER_TASK=50
 START_NUM=$(( $SLURM_ARRAY_TASK_ID * $PER_TASK ))
@@ -21,5 +22,5 @@ END_NUM=$(( ($SLURM_ARRAY_TASK_ID + 1) * $PER_TASK ))
 for (( run=$START_NUM; run<END_NUM; run++ )); do
 	RELEASE=${RELEASES_LIST[${run}]}
 
-	srun ./run_benchmark.sh $RELEASE
+	srun ./run_benchmark.sh $RELEASE $BENCH_BASE_DIR
 done

### 2021-08-23 scripts/benchmark_releases.sh

@@ -13,5 +13,6 @@ RELEASES_FILE=$USER_BASE_DIR/lz4releases
 
 RELEASES_LIST=($(<$RELEASES_FILE))
 RELEASE=${RELEASES_LIST[${SLURM_ARRAY_TASK_ID}]}
+BENCH_BASE_DIR=$USER_BASE_DIR/release_benchmark
 
-srun ./run_benchmark.sh $RELEASE
+srun ./run_benchmark.sh $RELEASE $BENCH_BASE_DIR

### 2021-08-23 scripts/run_benchmark.sh

@@ -3,18 +3,18 @@
 # This bash file builds and benchmarks lz4 against a specific commit
 
 USER=abeltluk
-USER_BASE_DIR=/scratch/$USER
+USER_BASE_DIR=/scratch/$USER/SystemsBenchmarking
 LZBENCH_DIR=$USER_BASE_DIR/lzbench
 LZ4_DIR=$USER_BASE_DIR/lz4
 SILESIA_DIR=$USER_BASE_DIR/silesia
 
 RELEASE=$1
 
-REL_BENCH_BASE_DIR=$USER_BASE_DIR/commit_benchmark
-WORKING_DIR=$REL_BENCH_BASE_DIR/build/$RELEASE
+BENCH_BASE_DIR=$2
+WORKING_DIR=$BENCH_BASE_DIR/build/$RELEASE
 
-RESULT_FILE=$REL_BENCH_BASE_DIR/results/$RELEASE.res
-TIMINGS_FILE=$REL_BENCH_BASE_DIR/results/$RELEASE.timings
+RESULT_FILE=$BENCH_BASE_DIR/results/$RELEASE.res
+TIMINGS_FILE=$BENCH_BASE_DIR/results/$RELEASE.timings
 
 # Setup environment
 mkdir $WORKING_DIR
@@ -40,7 +40,7 @@ cd ./lzbench
 make
 
 cd $WORKING_DIR
-# Run lzbench TODO
+# Run lzbench 
 ./lzbench/lzbench -elz4 -i10,10 -j -r -o4 -v silesia > $RESULT_FILE
 
 # Cleanup

### 2021-08-23 code/visualization/main.py
Added visualization code

@@ -2,6 +2,8 @@ import csv
 import os
 
 import matplotlib.pyplot as plt
+#from signal_processing_algorithms.energy_statistics import energy_statistics
+import numpy.random
 
 
 def plot_release_data():
@@ -20,13 +22,66 @@ def plot_release_data():
             compression_speed.append(float(line[1]))
             decompression_speed.append(float(line[2]))
 
-    plt.plot(labels, compression_speed)
+    plt.plot(labels, compression_speed,label="Compression speed")
     plt.ylabel('MB/s')
     plt.xlabel("Version")
     plt.ylim([0, 600.0])
     plt.xticks(rotation=90)
+    plt.legend()
     plt.tight_layout()
     plt.savefig("compression_plot.png")
+
+
+def plot_commit_data():
+    commit_res_dir = "../../results/commit_benchmark/"
+    commit_hash_file = "../../results/lz4commits_hashs"
+    compression_speed = []
+    decompression_speed = []
+
+    with open(commit_hash_file) as hash_file:
+        for commit_hash in hash_file:
+            if not os.path.isfile(os.path.join(commit_res_dir,commit_hash.strip()+".res")):
+                continue
+            with open(os.path.join(commit_res_dir,commit_hash.strip()+".res")) as commit_file:
+                reader = csv.reader(commit_file)
+                next(reader)
+                next(reader)
+                line = next(reader)
+                compression_speed.append(float(line[1]))
+                decompression_speed.append(float(line[2]))
+            #print(commit_hash.strip()+".res")
+
+        decompression_speed.reverse()
+        compression_speed.reverse()
+        plt.plot(compression_speed, label="Compression Speed")
+        plt.plot(decompression_speed, label="Decompression Speed")
+        plt.ylabel('MB/s')
+        plt.xlabel("# of commits since v1.8.1")
+        plt.ylim([0,4000])
+        plt.legend(loc=9)
+        #plt.axvline(x=3,color="r",lw=0.5,ls=":")
+        #plt.axvline(x=313,color="r",lw=0.5, ls=":")
+        plt.tight_layout()
+        plt.savefig("commits.png")
+
+
+def create_outlier():
+    numbers = numpy.random.uniform(0.95,1.05,200)
+    numbers = numpy.append(numbers, numpy.random.uniform(1.8,2.1,3))
[…]

### 2021-09-09 tex/paper.tex
Added base paper structure

--- 2021-08-23 tex/experiment_idea.tex
@@
 %*********************************************************************%
-\ifgerman{
-	\newcommand{\university}{Universität des Saarlandes}
-	\newcommand{\school}{Saarland Informatics Campus}
-}{
 \newcommand{\university}{Saarland University}
 \newcommand{\school}{Saarland Informatics Campus}
-}
-\ifgerman{ 
-	\newcommand{\thetitle}{Seminar: Title of the Seminar}
-	\newcommand{\shorttitle}{Seminar: Title of the Semianr}
-	\newcommand{\thedate}{18. Oktober}
-}{
 \newcommand{\thetitle}{Seminar: Systems Benchmarking}
@@
 \newcommand{\thegermandate}{15. April}
-}
 
@@
 % Advisors
-\ifgerman{
-	\newcommand{\advisor}{Betreuer}
-	}{
 	\newcommand{\advisor}{Advisors}
-	}
 	\newcommand{\advisors}{Prof. Sven Apel, \\ Christian Hechtl}
@@
 % Title for the seminar
-\ifgerman{
-	\newcommand{\theseminartitle}{Titel des Arbeit}
-}{
-	\newcommand{\theseminartitle}{"Performance Measurements Before Releases vs. Each Commits" -- Experiment Idea}
-}
+	%\newcommand{\theseminartitle}{"Performance Measurements Before Releases vs. Each Commits"}
+	\newcommand{\theseminartitle}{"Using Continuous Benchmarking in Productive Systems -- Opportunities and Challenges"}
 
@@
 
+% General Structure
+	% 1. Introduction and Motivation
+	% 2. General Definitions
+	%		2.1 What is a Benchmark
+	%		2.2 What is a continuous Benchmark
+	% 3. Experiment
+	%		3.1 Experiment Idea&Goals
+	%		3.2 Setup
+	%		3.3 Evaluation
+	%	4.
+
 	% Introduction
-	\ifgerman{\section{Einführung}}{\section{General}}
+	\section{General}
 	This document will briefly outline the experiment idea for the topic "Performance Measurements Before Releases vs.

### 2021-09-12 tex/paper.tex
Started on paper

@@
 	%\newcommand{\theseminartitle}{"Performance Measurements Before Releases vs. Each Commits"}
-	\newcommand{\theseminartitle}{"Using Continuous Benchmarking in Productive Systems -- Opportunities and Challenges"}
+	\newcommand{\theseminartitle}{"Using Benchmarking in Productive Development Systems -- Opportunities and Challenges"}
 
@@
 	% Introduction
-	\section{General}
-	This document will briefly outline the experiment idea for the topic "Performance Measurements Before Releases vs.
-Each Commits" in the seminar "Systems Benchmarking".
-The goal of this experiment and the corresponding paper is to showcase, how continous performance measurements throughout the whole development process can be used to detect and fix performance regressions at a very early stage.
+\section{Introduction}
+Over the past years system benchmarks have become more prominent in a variety of contexts and use cases.
+As a result more benchmarking tools became available that are used in both commercial systems and are widely adopted for academic purposes.
 
-	To achieve this, the experiment will first analyze the performance of public releases an open-source project to find a performance regression between two releases.
-Then, a performance measurement will be done for every commit between these two releases.
-We will use the data aquired by these performance measurements to demonstrate how or if various change detection measurements could havedetected this regression early on.
+In this paper we give an overview of the general concepts of system benchmarks before we consider in detail how classical benchmarking approaches can be used and extended to integrate it into the standard development process of software.
+Specifically, we take a look at how benchmark can be used to swiftly detect and react to performance changes throughout the development process.
+In order to do this we will take a look at Change-Point detection algorithms.
+We will outline and analyse the methodology and opportunities of such approaches while taking a careful look at the challenges that may arise due to this.
 
-\section{Experiment Setup}
+To support and evaluate our claims, we will conduct a practical experiment where we will use and compare several banchmarking techniques on a piece of well known, open-source software.
+TODO
 
-For my experiment I will use the open-source compression library \texttt{lz4}\footnote{\url{https://github.com/lz4/lz4}} as it has a active commit and release history.
-For the performance measurement itself we will use the latest version of the open-source project \texttt{lzbench}\footnote{https://github.com/inikep/lzbench}.
-Lzbench is an in-memory compression benchmarking tool that is originally designed to compare different compression algorithms.
-However for our case we will use it to simply only measure \texttt{lz4} at different releases/commits.
-For this case we will disable all other compression algorithms that \texttt{lzbench} supports at compile-time.
-First preliminary tests have shown that \texttt{lzbench} can easily use a different version of \texttt{lz4} than the shipped one by simply replacing the corresponding source files.
+\section{System Benchmarking}
+The term "Benchmark" is a rather broad term that can be interpeted and defined in many different ways depending on the context and application domain.
+We will use this chapter to give a definition of Benchmarking how we will use it throughout this paper.
 
-For the compression itself we will use the Silesia Data Corpus\footnote{http://sun.aei.polsl.pl/~sdeor/index.php?page=silesia}.
-The Sileasia Corpus combines a variety of different data in order to create a diverse dataset for compression measurements.
+\subsection{Definition}
+In standard literature a benchmark is commonly defined as "a tool coupled with a methodology for the evaluation and comparison of systems or components with respect to specific characteristice, such as performance, reliability or security." (\cite{sysbench} p.
+4).
 
-After identifying a performance regression between two releases we will collect data for the commits between these releases.
-To analyze the data collected for these commits we will compare the two following methods:
-\begin{itemize}
-	\item Comparing based on a static threshhold to the last commit/release
-	\item Using Change Point Detection (Specifically E-Divisive Means)\footnote{As described in \url{https://dl.acm.org/doi/pdf/10.1145/3358960.3375791}}
-\end{itemize}
+\subsection{Classification of Benchmarks}
 
-For the change point detection we will use the implementation provided by MongoDB\footnote{https://github.com/mongodb/signal-processing-algorithms}.
-Since we will also store the raw performance data as returned by \texttt{lzbench} it is also possible to add further methods later on to get a better overview of different methods.
+\subsection{Evaluating Benchamrks}
 
-\section{Challenges and possible risks}
-In this section I will briefly outline challenges, risks that might arise during the experiment and also outline possible solutions to them.
+\section{Detecting Performance Changes}
 
-\subsection{Detecting regression between releases}
-\subsubsection{Defining a regression threshhold}
-One of the main challenges will be to define a threshhold for a performance regression between commits.
-As a first starter we will work with a static threshhold of 10\% as compared to the previous release.
-However if this value seems to many/less releases we might need to change the threshhold or overthink out strategy overall.
+\section{Continuous Benchmarking}
+\subsection{Definition}
+\subsection{Usages}
+\subsection{Challenges}
 
-\subsubsection{No regression detected}
-It might happen that we will detect no noticable performance changes whatsoever between the individual releases.
-One likely reason for this might be that the actual performance regressions happened while testing the release and where therefore fixed in the actual release.
+\section{Experiment}
+	\subsection{Experiment Idea \& Goals}
+	\subsection{Experiment Setup}
+	\subsection{Experiment Results}
 
-One solution to this might be to select some commit for measurement before the release commit to benchmark on.
-However this would require a lot of manual triaging to select the "correct" commit based on e.g.
-the commit or issue history of the project.
+\section{Evaluation of Performance Results}
 
-Then still it could happen that with that strategy we do not detect any performance regressions (or improvements) that we can use as a guideline where to perform our finer measurement.
-In that case we could:
-\begin{itemize}
-	\item Select an arbitrary release range for our finer analysis -- However this itself bears the risk that we do not detect any change points in this range
-	\item Select a release range based on issues submitted on the GitHub page that indicate that there at least was some performance regression during this period
-	\item Select another project for our experiment
-\end{itemize}
+\section{Reflection}
 
-\subsection{Measuring individual commits}
-
-\subsubsection{Commits that won't build}
-If we measure all commits between two releases it is very likely that not all commits will be able to compile.
-We can easily take this into account by simply skipping these commits and not perform any measurements if we detect a failure during build.
-
-\subsubsection{Number of commits}
-Even when restricting us to the duration between two releases it might still happen that we end up with a lot of commits we need to benchmark individually.
-Depending how long one benchmark takes this could easily take too much time to finish in a reasonable time frame.
-Additionally we have to remember that also others might want to use the cluster environment for their experiments, so we should not clog it with hundreds of our jobs.
-
-One possible measure to counteract this is to not measure each individual commit but squash them based on some criterion, e.g.
-only measuring one commit per day.
-In practice we will have to take a close look how long an individual performance measurement (including build etc.) takes so that we can esitmate how long our measurements would take in total.
-
-\section{Possible Extensions}
-There are a few possible extensions that could be appended to this experiment idea if time allows it:
-\begin{itemize}
-	\item Using the data collected by individual commits to show how individual commits can be compared effectively\footnote{As shown in \url{https://arxiv.org/pdf/2101.10231.pdf}}
-	\item Extend the regression detection method
-	\item Evaluate the impact on sustainability
-\end{itemize}
+\section{Future Work}
 

### 2021-09-12 tex/paper.tex
Minor additions to paper draft

@@
 \usepackage{amssymb}
+\usepackage{hyperref}
 
@@
 
-\ifgerman{
-	\usepackage[ngerman]{babel}
-	\usepackage{ngerman}
-	\usepackage{bibgerm}        % German symbols in BibTeX
-}{
 \usepackage[english]{babel}
-}
 
@@
 
-\section{System Benchmarking}
-The term "Benchmark" is a rather broad term that can be interpeted and defined in many different ways depending on the context and application domain.
+\section{System Benchmarks}
+\label{sec:benchmarking}
+The term "Benchmark" is a broad term that can be interpeted and defined in many different ways depending on the context and application domain.
 We will use this chapter to give a definition of Benchmarking how we will use it throughout this paper.
@@
 \subsection{Definition}
-In standard literature a benchmark is commonly defined as "a tool coupled with a methodology for the evaluation and comparison of systems or components with respect to specific characteristice, such as performance, reliability or security." (\cite{sysbench} p.
+\label{ssec:bench_definition}
+The term "Benchmark" is used in a variaty of different domains and, according to the Standard Specialization Evalutation Corporation, historically stems from a physical marking that was used as a refernce point on a workbench to check the length of the produced pieces\footnote{SPEC Glossary: \url{https://www.spec.org/spec/glossary/\#benchmark}}.
+However throughout this paper we are only interested in system benchmarks within the context of software systems and will therefore also refer to the definition of a benchmark as given by Kounev et al.: "a tool coupled with a methodology for the evaluation and comparison of systems or components with respect to specific characteristics, such as performance, reliability or security." (\cite{Kounev} p.
 4).
+As already given from this definition benchmarks can serve as an evaluation for different characteristics.
+We will more closely look at these in \autoref{ssec:bench_classification}.
+Throughout this paper we will also mostly refer to the "system or component" that is being benachmarked as the \textit{System under Test} (SUT).
 
 \subsection{Classification of Benchmarks}
+\label{ssec:bench_classification}
 
-\subsection{Evaluating Benchamrks}
+\subsection{Evaluating Benchmarks}
 
@@
 	% As a recommendation JabRef might be a usefull tool for this section. Use myRefs.bib therefore
-
+	\phantomsection
+	\bibliographystyle{splncs03}
+	\bibliography{literature}	
 \end{document}

### 2021-09-13 scripts/benchmark_commits.sh
Minor restructuring of repository
Adapted some paths in scripts

@@ -5,15 +5,15 @@
 #SBATCH --constraint=kine
 #SBATCH --array=0-6
 #SBATCH --time=02:00:00
-#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4commits/commit_benchmark_%A_%a.out
-#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4commits/commit_benchmark_%A_%a.err
+#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4commits/%A/commit_benchmark_%A_%a.out
+#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4commits/%A/commit_benchmark_%A_%a.err
 
 USER=abeltluk
 USER_BASE_DIR=/scratch/$USER
 RELEASES_FILE=$USER_BASE_DIR/lz4commits
 
 RELEASES_LIST=($(<$RELEASES_FILE))
-BENCH_BASE_DIR=$USER_BASE_DIR/commit_benchmark
+BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/commit_benchmark
 
 PER_TASK=50
 START_NUM=$(( $SLURM_ARRAY_TASK_ID * $PER_TASK ))

### 2021-09-13 scripts/benchmark_releases.sh

@@ -4,12 +4,12 @@
 #SBATCH --partition=seminar
 #SBATCH --constraint=kine
 #SBATCH --array=0-12
-#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4releases/release_benchmark_%A_%a.out
-#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4releases/release_benchmark_%A_%a.err
+#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4releases/%A/release_benchmark_%A_%a.out
+#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4releases/%A/release_benchmark_%A_%a.err
 
 USER=abeltluk
 USER_BASE_DIR=/scratch/$USER
-RELEASES_FILE=$USER_BASE_DIR/lz4releases
+RELEASES_FILE=$USER_BASE_DIR/SystemsBenchmarking/benchmark/lz4releases
 
 RELEASES_LIST=($(<$RELEASES_FILE))
 RELEASE=${RELEASES_LIST[${SLURM_ARRAY_TASK_ID}]}

### 2021-09-13 scripts/run_benchmark.sh

@@ -41,7 +41,7 @@ make
 
 cd $WORKING_DIR
 # Run lzbench 
-./lzbench/lzbench -elz4 -i10,10 -j -r -o4 -v silesia > $RESULT_FILE
+./lzbench/lzbench -elz4 -i100,100 -p3 -j -r -o4 -v silesia > $RESULT_FILE
 
 # Cleanup
 cd $USER_BASE_DIR

### 2021-09-13 scripts/benchmark_releases.sh
Slight change in benchmark script

@@ -4,8 +4,8 @@
 #SBATCH --partition=seminar
 #SBATCH --constraint=kine
 #SBATCH --array=0-12
-#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4releases/%A/release_benchmark_%A_%a.out
-#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4releases/%A/release_benchmark_%A_%a.err
+#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4releases/release_benchmark_%A_%a.out
+#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4releases/release_benchmark_%A_%a.err
 
 USER=abeltluk
 USER_BASE_DIR=/scratch/$USER
@@ -13,6 +13,6 @@ RELEASES_FILE=$USER_BASE_DIR/SystemsBenchmarking/benchmark/lz4releases
 
 RELEASES_LIST=($(<$RELEASES_FILE))
 RELEASE=${RELEASES_LIST[${SLURM_ARRAY_TASK_ID}]}
-BENCH_BASE_DIR=$USER_BASE_DIR/release_benchmark
+BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/release_benchmark
 
 srun ./run_benchmark.sh $RELEASE $BENCH_BASE_DIR

### 2021-09-13 scripts/benchmark_commits.sh
Fixed path in commit benchmark script

@@ -4,13 +4,13 @@
 #SBATCH --partition=seminar
 #SBATCH --constraint=kine
 #SBATCH --array=0-6
-#SBATCH --time=02:00:00
-#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4commits/%A/commit_benchmark_%A_%a.out
-#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4commits/%A/commit_benchmark_%A_%a.err
+#SBATCH --time=12:00:00
+#SBATCH --output=/scratch/abeltluk/slurm_logs/lz4commits/commit_benchmark_%A_%a.out
+#SBATCH --error=/scratch/abeltluk/slurm_logs/lz4commits/commit_benchmark_%A_%a.err
 
 USER=abeltluk
 USER_BASE_DIR=/scratch/$USER
-RELEASES_FILE=$USER_BASE_DIR/lz4commits
+RELEASES_FILE=$USER_BASE_DIR/SystemsBenchmarking/benchmark/lz4commits
 
 RELEASES_LIST=($(<$RELEASES_FILE))
 BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/commit_benchmark

### 2021-09-14 tex/paper.tex
* Started section on classifications of benchmarks
+ Added glossary file

@@
 
+\usepackage{glossaries}
+
+\makeglossaries
+
+\loadglsentries{glossary}
 %*********************************************************************%
@@
 We will more closely look at these in \autoref{ssec:bench_classification}.
-Throughout this paper we will also mostly refer to the "system or component" that is being benachmarked as the \textit{System under Test} (SUT).
+Throughout this paper we will also mostly refer to the "system or component" that is being benachmarked as the \gls{sut}.
 
@@
 \label{ssec:bench_classification}
+Benchmarks can be classified in a variety of different means. In this section we will give a small overview of the different types of benchmarks there are with respect to the following questions:
+\begin{enumerate}
+	\item What overall goal does a benchmark serve?
+	\item What qualities are evaluated by an benchmark?
+	\item How can a benchmark be performed (Benchmarking strategies)
+\end{enumerate}
+
+In the broadest sense, benchmarks can be divided into competetive and non-competetive benchmarks.
+The main motivation of competetive benchmarks is hereby the development of standardized quality criteria that can be used to compare different systems.
+Certain sources also emphasize this importance on the competetiveness by providing a more detailled definition of the term benchmark, i.e.
+"a standard tool for competetive evaluation and comparison of competetive systems" (\cite{kistowski2015} p.
+X).
+
+For non-competetive benchmarks Kounev et al. Further distiguish between the two categories of "rating tools" and "research benchmark.
 

### 2021-09-14 tex/paper.tex
Finished subsection for classification of benchmarks

@@
 \label{ssec:bench_classification}
-Benchmarks can be classified in a variety of different means. In this section we will give a small overview of the different types of benchmarks there are with respect to the following questions:
+Benchmarks can be classified in a variety of different means. In this section we will give a small overview of the different types of benchmarks there are with respect to the two following questions:
 \begin{enumerate}
@@
 
-For non-competetive benchmarks Kounev et al. Further distiguish between the two categories of "rating tools" and "research benchmark.
+For non-competetive benchmarks Kounev et al.
+Further distiguish between the two categories of "rating tools" and "research benchmark".
+Rating tools can serve multiple purposes: Either as a component of an development and system improvement process, as a baseline for regulatory programmes or to serve as common benchmark for research.
+Research benchmarks on the other hand commonly refer to tools and workloads that may be used for in-depth evaluation of research results, prototypes or productive systems.
+Based on these descriptions it becomes apparent that there sometimes might be no clear distinction between a rating tool and a research benchmark and the terminology is often determined by the evaluating party (See \cite{Kounev} p.
+4).
+
+Regardless of the competetiveness, or lack thereof, of a benchmark the key metrics that are evaluated are often similar or even identical.
+While historically the main metrics of importance were e.g.
+security, system reliability and energy efficiency, modern benchmarks also try to cover much more aspects of a software.
+We will discuss a selection of the quality attributes listed by Kounev et al.
+that are usually target of modern benchmarks(\cite{Kounev} p.
+6 f):
+
+\paragraph{Performance} The term Performance itself can be interpreted in many different means.
+For this paper, we will focus on one of the most basic interpretations: The amount of work done compared to the time and resources used.
+A much more in-depth explanation of different performance measures is given by Kounev et al.
+(See \cite{Kounev} p.
+49 ff)
+
+\paragraph{Scalability} TODO Definition needed
+
+\paragraph{Energy Efficiency} TODO Definition needed
+
+\paragraph{Reliability} TODO Definition needed
+
+When it comes to benchmarking strategies two approaches are most prominent: Fixed-Time and Fixed-Work benchmarks.
+A Fixed-Work Benchmark here describes the most intuitive approach for benchmarking: We fix a specified amount of work $W_i$ and measure the required time $T_i$ that is required to fulfill this work.
+
+While Fixed-Work benchmarks are easy to understand and implement, it introduces an implicit performance bottleneck that is also known as \textit{Amdahl's Law}.
+It states that the maximum possible performance improvement that can be achieved in Fixed-Work Benchmarks is prohibitly upper-bounded by the fraction of work that is performed by the component that is being improved (See \cite{Kounev} p.
+9f).
+
+In Fixed-Time benchmarks, instead of fixing the amount of work $W_i$, the time $T_i$ is bound and the amount of work finished in this time is measured as a metric.
+As opposed to Fixed-Work Benchmarks the Fixed-Time Benchmarks do not suffer the issue of an upper-bounded maximum improvement as for every improvement, the reduced time can be used to process further work units (See \cite{Kounev} p.
+11).
 

### 2021-09-15 tex/paper.tex
Finished general chapter about benchmarks

@@
 
+Additionally there are also further approaches that does not employ fixed time or work at all, but rather employ variable-time and -work characteristics.
+For this case the matric is a function of the time $T$ and the work $W$.
+While this technique provides maximum flexibility, this approach is not suitable for all types of benchmarks (See \cite{Kounev} p.
+12)
+
 \subsection{Evaluating Benchmarks}
+
+Apart from the metrics that evaluate the result of a benchmark, there are also several attributes that are important to evaluate the quality of the benchmark itself.
+The designer of a benchmark should always take these attributes into consideration when creating a benchmark.
+As described by Skadron et al.
+it is not possible to create a single benchmark that covers all these attributes perfectly.
+Therefore one either has to create mutliple benchmarks that complement each others weaknesses or choose to sacrifice one of these attributes over the other (\cite{Skadron2003} p.
+32f).
+
+Over the years, researchers and industry associates alike have defined several criteria that are considered desirable by modern standards.
+Often the exact terminology of these criteria differs based on authors and the specific application domain, however the concepts in general are similar.
+Kounev at al.
+list five core criteria that will be defined in a little more detail in this chapter (\cite{Kounev} p.
+13f).
+A much more in depth discussion of these criteria was performed by Kistowski et al.
+(See \cite{kistowski2015})
+
+\paragraph{Relevance} TODO: Short explanation
+\paragraph{Reproducibility} TODO: Short explanation
+\paragraph{Fairness} TODO: Short explanation
+\paragraph{Verifiability} TODO: Short explanation
+\paragraph{Usability} TODO: Short explanation
 
@@
 \section{Experiment}
+
 	\subsection{Experiment Idea \& Goals}

### 2021-09-15 tex/paper.tex
Added further explanation for evaluation of benchmarks

@@
 \newcommand{\shorttitle}{Seminar: Systems Benchmarking}
-\newcommand{\thedate}{April 15}
+\newcommand{\thedate}{\today{}}
 \newcommand{\thegermandate}{15. April}
@@
 
-\paragraph{Relevance} TODO: Short explanation
-\paragraph{Reproducibility} TODO: Short explanation
+\paragraph{Relevance} For a benchmark to be meaningful it is important that it, at least to a certain extent, reproduces some scenarios with real world application.
+This is what the "Relevance" of a benchmark refers to.
+It tries to define how relevant the produced information is to a potential user of a software.
+According to Kistowski et al.
+this makes it "perhaps the most important characteristic" (\cite{kistowski2015} p.
+334).
+However the relevance of a benchmark may also limits the benchmarks applicability meaning, that a highly relevant benchmark for a specific system or component might only narrow applicability while benchmarks with a broad applicability will have a lower relevance but for a wider selection of applications.
+Kitowski et al.
+further elaborate on this with specific examples (\cite{kitowski2015} p.
+334f)
+
+\paragraph{Reproducibility} Reproducability ensures that it is possible for a third party to produce ideally the same results for a given test environment.
+Reproducability covers both the consistency between mutliple runs on the same system as well as creating the same results on another environment with a semantically equivalent configuration.
+
+However, with modern hard- and software systems, optimal reproducability has become challenging.
+For both hard- and software there are several factors that induce variability.
+From a hardware side things such as the physical disc layout or network connections may affect benchmarking results.
+For software systems the causes for variability stem from various different sources.
+from a low-level perspective, things such as thread scheduling can influence the benchmark results.
+From a higher level perspective a benchmark has to consider the configurability of a software system itself.
+Modern software systems often offer lots of different configuration options which can be used to create a tailor made system-variant.
+En- or disabling a specific feature might heavily influence the performance of a benchmark.
+
+According to Huppler, an ideal benchmark result should be definable as a function fo a hard- and software configuration (See \cite{huppler2009} p.
+335).
+However for real-world applications, modelling such a function is far too complex which requires the benchmark designer to try to model reproducability in other ways.
+In the end the reproducability of a benchmark is heavuly dependent on the ability to reproduce the benchamrking environment that was used to create this specific benchmark.
+
 \paragraph{Fairness} TODO: Short explanation
@@
 \subsection{Definition}
-\subsection{Usages}
+\subsection{Strategies and Opportunities}
 \subsection{Challenges}

### 2021-09-15 tex/paper.tex
Started on experiment description

@@
 \section{Experiment}
+In this chapter we will further elaborate on the experiment that was conducted.
+The chapter will give an overview over the general experiment idea and it's goals, the experiment setup and the specific results that were achieved in the experiment runs.
+An in-depth analysis and evaluation of the experiment results is performed in \autoref{sec:exp_evaluation}
 
 	\subsection{Experiment Idea \& Goals}
+	The main idea of the experiment that was created was to perform a benchmark on a series of versions of a specific open-source software to evaluate the methods and techniques described in this paper.
+More specifically, we want to evaluate the following questions:
+	\begin{itemize}
+		\item When do we need to benchmark software?
+			\begin{itemize}
+				\item Is it sufficient to benchmark releases?
+				\item Do we need to benchmark every commit?
+			\end{itemize}
+		\item How do different continuous benchmarking approaches compare with respect to:
+			\begin{itemize}
+				\item Complexity of implementation?
+				\item Reliably detecting performance changes?
+				\item Reducing the amount of manual work required by the developer?
+			\end{itemize}
+	\end{itemize}
+
+	Additionally the experiment should also be used to identify other, currently unidentified, challenges and opportunities that this approach might offer.
+
+	For the first complex of the questions mentioned above, the follwoing methology is planned: Firstly, perform a benchmark of all public releases on the open-source software that was selected.
+In a second step then every individual commit is benchmarked for more fine-grained data.
+By comparing the performance results of the pure release benchmarking and the individual commit benchmarking it is eventually possible to decide if a specific performance regression could have been detected earlier if a continuous benchmarking approach would have been used.
+
 	\subsection{Experiment Setup}
+
 	\subsection{Experiment Results}
@@
 \section{Evaluation of Performance Results}
-
+\label{sec:exp_evaluation}
 \section{Reflection}

### 2021-09-20 tex/paper.tex
Started chapter about benchmarking approaches

@@
 % Title for the seminar
-	%\newcommand{\theseminartitle}{"Performance Measurements Before Releases vs. Each Commits"}
-	\newcommand{\theseminartitle}{"Using Benchmarking in Productive Development Systems -- Opportunities and Challenges"}
+\newcommand{\theseminartitle}{"Performance Measurements Before Releases vs. Each Commits"}
+%\newcommand{\theseminartitle}{"Using Benchmarking in Productive Development Systems -- Opportunities and Challenges"}
 
@@
 
-\section{Detecting Performance Changes}
+\section{Using Benchmarks to Detect Performance Changes}
+\label{sec:bench_perf_changes}
+	This section will discuss how benchmarks can be used during software development to detect performance changes.
 
-\section{Continuous Benchmarking}
-\subsection{Definition}
-\subsection{Strategies and Opportunities}
-\subsection{Challenges}
+	\subsection{Opportunities}
+	\label{ssec:bench_perf_oppo}
+	While benchmarks as a standalone tooling are alreay a useful tool to compare the performance of different systems in order to, for example, select a specific system for a given task it also offers different opportunities.
+One of these opportunities is to use benchmarking as a tool that is closely integrated into the development cycle in order to evaluate the systems performance throughout the development.
+
+	There are different goals to consider when integrating benchmarking into the development process.
+Most prominently benchmarking can be used as a quality measure to evaluate a software systems performance.
+Due to the increasing complexity in modern software systems it is often not possible to foresee the impact of even a small change to the performance of a complex software system (See \cite{grambow2019} p.
+1, \cite{daly2021} p.
+1).
+
+	As a result if not including any performance evaluation might lead to performance regressions being shipped in a stable release to customers and users.
+Therefore using benchmarks throughout the development process can ensure to detect performance changes and allows to fix them before they are being released (See \cite{daly2021} p.
+1).
+
+	Additionally employing benchmark on a regular basis also opens the window of opportunity for many other improvements if the corresponding infrastructure is setup accordingly.
+Daly describes in great detail how this was achieved for the MongoDB infrastructure in \cite{daly2021}.
+In summary the following have been observed:
+	\begin{itemize}
+		\item Increased productivity of the developers
+		\item Reduced noise on the performance data
+		\item Improved Comparison of arbitrary results
+		\item An increased amount of performance improvements
+	\end{itemize}
+
+	For this chapter we want to focus on two main questions; How can performance benchmarking be used to:
+	\begin{enumerate}
+		\item Quickly and reliably detect performance changes?
+		\item Compare arbitrary development states?
+	\end{enumerate}
+
+	The underlying overall question however is, when or how often, one needs to perform a benchmark in order to sufficiently answer these questions.
+For this two approaches will be compared in the following subsections:
+	\begin{enumerate}
+		\item Benchmarking Before Publishing a new Release
+		\item Benchmarking Every Commit -- Which we will refer to a \textit{Continuous Benchmarking}
+	\end{enumerate}
+
+	\subsection{Benchmarking Before Releases}
+	The most intuitive approach to ensure the performance of a software system throughout the release history is quite simple: Based on the requirements imposed by either a customer or internal quality assurance one defines certain performance threshhold that the software needs to fulfill.
+Based on these quality criteria the development team can build a benchmark that can check these attributes.
+
+	When
+
+	\subsection{Continuous Benchmarking}
+		\subsubsection{Definition}
+		\subsubsection{Strategies}
+		\subsubsection{Opportunities and Challenges}
 
@@
 	\subsection{Experiment Idea \& Goals}
+	\label{ssec:exp_goals}
+
 	The main idea of the experiment that was created was to perform a benchmark on a series of versions of a specific open-source software to evaluate the methods and techniques described in this paper.
@@
 				\item Reducing the amount of manual work required by the developer?
+				\item Can we use this metric to compare arbitrary commits?
 			\end{itemize}
@@
 	\subsection{Experiment Setup}
+	\label{ssec:exp_setup}
+
+	To perform the experiment as described in \autoref{ssec:exp_goals} the open-source software LZ4\footnote{\url{https://github.com/lz4/lz4}} will be used.
+\texttt{LZ4} is a compression library with an active commit history.
+In total \texttt{LZ4} offers 31 releases and more than 2500 commits in total\footnote{As of 16.09.2021}.
+
+	For the benchmark itself the open source project \texttt{lzbench}\footnote{\url{https://github.com/inikep/lzbench}} will be used.
+Lzbench is an in-memory compression benchmarking tool that is designed to compare different implementations of compression algorithms.
+For this experiment all other compression algorithm implementations will be disabled so that only \texttt{lz4} will be benachmarked at different releases and commits.
+
+	Lzbench offers the option to disable all the other compression algorithms at compile time.
+The LZ4 version that is used for the benchmark can simply be changed by overwriting the corresponding lz4 files within the lzbench repository before compilation.
+In the experiment a slightly adapted version of Lzbench will be used that has the other compression algorithms disabled at compile time and also incorporates some minor changes that were required to ensure compilation on the cluster infrastructure.
+
+	Lzbench also offers a variety of command line switches that influence the behavior of the benchmark.
+An overview of the switches that were used for executing this experiment can be found in \autoref{tab:cmd_switches}\footnote{Also see: \url{https://github.com/inikep/lzbench}}.
+
+	\begin{table}
+		\caption{Overview of used command line switches for lzbench}
+		\label{tab:cmd_switches}
+		\centering
+		\begin{tabular}{|c|c|}
+			\hline
+			\textbf{Switch} & \textbf{Description}\\
+			\hline\hline
+			\texttt{-elz4} & Limits the lzbench run to only benchmark the lz4 compression implementation \\
+			\hline
+			\texttt{-i100,100} & Sets the minimum number of compression and decompression iterations to $100$ \\
+			\hline
+			\texttt{-p3} & Sets the output to print the median speed of all iterations \\
+			\hline
+			\texttt{-j} & Join files in memory but compress them independently \\
+			\hline
+			\texttt{-r} & Operate recursively on directories \\
+			\hline 
+			\texttt{-o4} & Sets the output text format to CSV \\
+			\hline
+			\texttt{-v} & Disables progress information \\
+			\hline
+		\end{tabular}
+	\end{table}
+
+	As a workload for the compression benchmark the Silesia Data Corpus will be used\footnote{\url{http://sun.aei.polsl.pl/~sdeor/index.php?page=silesia}}.
+The Silesia Corpus is a diverse dataset that has specifically been designed as a compression workload with the motivation in mind to include a variety of different data sources.
+By this the Silesia Corpus tries to not favor any compression algorithms that perform very well on a certain type of data(TODO: Citation needed).
+
+Since the LZ4 repository consists of over 2500 commits benchmarking each individual commit is infeasible for the scope of this paper as it would both generate too much data to evaluate properly as well as strain the available shared server resources too much.
+Therefore a two staged approach will be used:
+\begin{itemize}
+	\item In the first step, a benchmark will be performed on the publicly available releases\footnote{Based on the tags created in the GitHub repository}.
+The results of these benchmarks will be used to identify a commit range with a significant performance change
+	\item All commits in the identified commit range will be benchmarked for a more detailed and thourough analysis.
+\end{itemize}
+
+The benchmark itself will be performed on the Cluster Infrastructure of the Software Engineering Chair of Saarland University using Slurm\footnote{See \url{https://slurm.schedmd.com/documentation.html}}.
+The machines that are used are part of the \texttt{kine} cluster with the following hardware configuration\footnote{CPU Information has been aquired using the \texttt{lscpu} command}:
+
+\begin{itemize}
+	\item CPU Model: Intel(R) Xeon(R) CPU E5-2630 v4 @ 2.20GHz
+	\item Cores per Socket: $10$
+	\item Number of Sockets: $2$
+	\item Minimum CPU Frequency: $1200$ MHz
+	\item Maximum CPU Frequency: $3200$ MHz
+	\item Available RAM: 256 GB
+\end{itemize}
+
+For the performance change detection up to three different approaches to compare the benchmarking data will be presented.
+Based on the results of these approaches the questions posed in \autoref{ssec:exp_goals} will be evaluated and compared.
+The approaches used are defined in detail in \autoref{sec:exp_evaluation}.
 

### 2021-09-21 code/visualization/main.py
Minor updates to uild script and visualizations

@@ -2,12 +2,12 @@ import csv
 import os
 
 import matplotlib.pyplot as plt
-#from signal_processing_algorithms.energy_statistics import energy_statistics
+from signal_processing_algorithms.energy_statistics import energy_statistics
 import numpy.random
 
 
 def plot_release_data():
-    release_res_dir = "../../results/releases_benchmark/"
+    release_res_dir = "../../release_benchmark/mintime/results"
     labels = []
     compression_speed = []
     decompression_speed = []
@@ -22,21 +22,29 @@ def plot_release_data():
             compression_speed.append(float(line[1]))
             decompression_speed.append(float(line[2]))
 
-    plt.plot(labels, compression_speed,label="Compression speed")
+    decompression_speed.sort(key=dict(zip(decompression_speed,labels)).get)
+    compression_speed.sort(key=dict(zip(compression_speed,labels)).get)
+    labels.sort()
+
+    plt.plot(labels, decompression_speed,label="Decompression speed",color="orange")
     plt.ylabel('MB/s')
     plt.xlabel("Version")
-    plt.ylim([0, 600.0])
+    plt.ylim([0, 4000.0])
     plt.xticks(rotation=90)
+
+    #plt.clf()
+    plt.plot(labels, compression_speed, label="Compression speed")
     plt.legend()
     plt.tight_layout()
-    plt.savefig("compression_plot.png")
+    plt.savefig("releases_plot.png")
 
 
 def plot_commit_data():
-    commit_res_dir = "../../results/commit_benchmark/"
-    commit_hash_file = "../../results/lz4commits_hashs"
+    commit_res_dir = "../../commit_benchmark/mintime/results/"
+    commit_hash_file = "../../benchmark/merge_commits"
     compression_speed = []
     decompression_speed = []
+    labels = []
 
     with open(commit_hash_file) as hash_file:
         for commit_hash in hash_file:
@@ -44,6 +52,7 @@ def plot_commit_data():
                 continue
             with open(os.path.join(commit_res_dir,commit_hash.strip()+".res")) as commit_file:
                 reader = csv.reader(commit_file)
+                labels.append(commit_hash)
                 next(reader)
                 next(reader)
                 line = next(reader)
@@ -59,10 +68,26 @@ def plot_commit_data():
         plt.xlabel("# of commits since v1.8.1")
         plt.ylim([0,4000])
[…]

### 2021-09-21 tex/paper.tex
Finished chapter about benchmarking before releases

@@
 	\subsection{Benchmarking Before Releases}
-	The most intuitive approach to ensure the performance of a software system throughout the release history is quite simple: Based on the requirements imposed by either a customer or internal quality assurance one defines certain performance threshhold that the software needs to fulfill.
+	The most intuitive approach to ensure the performance of a software system throughout the release history is quite simple: Based on the requirements imposed by either a customer or internal quality assurance one defines certain performance threshold that the software needs to fulfil.
 Based on these quality criteria the development team can build a benchmark that can check these attributes.
 
-	When
+	Once the software is nearing a new release and e.g.
+a new \textit{Release Candidate} is created internally, the development team can use this benchmark to evaluate whether the candidate introduces a performance regression or if it is fit for a release.
+There are several benefits of this approach; First of all, it does not necessarily requires an automated performance testing infrastructure but rather can be executed and evaluated manually be the development team.
+
+	However this approach also bears various challenges that need to be considered in the development of modern software systems.
+Daly describes two main challenges that arose when using this approach in the development of MongoDB: Firstly it is possible that test from the last release cycle are simply not reproducible with the current software, secondly identifying the exact change that introduced a performance regression poses challenging (\cite{daly2021} p.
+1f).
+
+	Both of these challenges are heavily influenced by the length of software release cycles and the resulting amount of commits throughout one cycle.
+As an example one can take a look at a few open-source repositories.
+The C++ test framework \textit{googletest}\footnote{See \url{https://github.com/google/googletest}} by Google with it's most recent release (\textit{1.11.0}) in June 2021, while the last release before that (\textit{1.10.0}) was released in October 2019.
+During this period of 28 months roughly 700 commits have been added to the repository.
+Similarly for the C implementation of the LZ4 compression algorithm that can be found on GitHub\footnote{\url{https://github.com/lz4/lz4}} in the 15 months between the two most recent releases about 250 commits have been added to the code.
+
+	This can also be observed in commercially used software such as MongoDB which reported about 5500 commits to their code throughout the 2019/2020 release cycle averaging to just about 15 commits per day (\cite{daly2021} p.
+2).
+If the only benchmarking data available is these from the two release candidates this results in an extensive additional overhead to retroactively reconstruct the cause of the root cause.
+
+	One additional dimension that has to be considered is the aspect of configurability.
+In modern software systems there are often configuration options available which allows to en- and disable certain features to create a tailor-made system variant.
+However, this additional layer of complexity adds further challenges to benchmarking and change detection.
+As already very few configuration options lead to an combinatorial explosion of the possible system variants which makes it unfeasible to benchmark all of them(See \cite{apel2020} p.
+1).
 
 	\subsection{Continuous Benchmarking}
-		\subsubsection{Definition}
+
+	\subsubsection{Motivation \& Definition}
 		\subsubsection{Strategies}

### 2021-09-21 tex/paper.tex
Fixed some spelling mistakes

@@
 
-To support and evaluate our claims, we will conduct a practical experiment where we will use and compare several banchmarking techniques on a piece of well known, open-source software.
-TODO
+To support and evaluate our claims, we will conduct a practical experiment where we will use and compare several benchmarking techniques on a piece of well known, open-source software.
 
@@
 \label{sec:benchmarking}
-The term "Benchmark" is a broad term that can be interpeted and defined in many different ways depending on the context and application domain.
+The term "Benchmark" is a broad term that can be interpreted and defined in many different ways depending on the context and application domain.
 We will use this chapter to give a definition of Benchmarking how we will use it throughout this paper.
@@
 \label{ssec:bench_definition}
-The term "Benchmark" is used in a variaty of different domains and, according to the Standard Specialization Evalutation Corporation, historically stems from a physical marking that was used as a refernce point on a workbench to check the length of the produced pieces\footnote{SPEC Glossary: \url{https://www.spec.org/spec/glossary/\#benchmark}}.
+The term "Benchmark" is used in a variety of different domains and, according to the Standard Specialization Evaluation Corporation, historically stems from a physical marking that was used as a reference point on a workbench to check the length of the produced pieces\footnote{SPEC Glossary: \url{https://www.spec.org/spec/glossary/\#benchmark}}.
 However throughout this paper we are only interested in system benchmarks within the context of software systems and will therefore also refer to the definition of a benchmark as given by Kounev et al.: "a tool coupled with a methodology for the evaluation and comparison of systems or components with respect to specific characteristics, such as performance, reliability or security." (\cite{Kounev} p.
@@
 We will more closely look at these in \autoref{ssec:bench_classification}.
-Throughout this paper we will also mostly refer to the "system or component" that is being benachmarked as the \gls{sut}.
+Throughout this paper we will also mostly refer to the "system or component" that is being benchmarked as the \gls{sut}.
 
@@
 
-In the broadest sense, benchmarks can be divided into competetive and non-competetive benchmarks.
-The main motivation of competetive benchmarks is hereby the development of standardized quality criteria that can be used to compare different systems.
-Certain sources also emphasize this importance on the competetiveness by providing a more detailled definition of the term benchmark, i.e.
-"a standard tool for competetive evaluation and comparison of competetive systems" (\cite{kistowski2015} p.
+In the broadest sense, benchmarks can be divided into competitive and non-competitive benchmarks.
+The main motivation of competitive benchmarks is hereby the development of standardized quality criteria that can be used to compare different systems.
+Certain sources also emphasize this importance on the competitiveness by providing a more detailed definition of the term benchmark, i.e.
+"a standard tool for competitive evaluation and comparison of competitive systems" (\cite{kistowski2015} p.
 X).
 
-For non-competetive benchmarks Kounev et al.
-Further distiguish between the two categories of "rating tools" and "research benchmark".
+For non-competitive benchmarks Kounev et al.
+Further distinguish between the two categories of "rating tools" and "research benchmark".
 Rating tools can serve multiple purposes: Either as a component of an development and system improvement process, as a baseline for regulatory programmes or to serve as common benchmark for research.
@@
 
-Regardless of the competetiveness, or lack thereof, of a benchmark the key metrics that are evaluated are often similar or even identical.
+Regardless of the competitiveness, or lack thereof, of a benchmark the key metrics that are evaluated are often similar or even identical.
 While historically the main metrics of importance were e.g.
@@
 When it comes to benchmarking strategies two approaches are most prominent: Fixed-Time and Fixed-Work benchmarks.
-A Fixed-Work Benchmark here describes the most intuitive approach for benchmarking: We fix a specified amount of work $W_i$ and measure the required time $T_i$ that is required to fulfill this work.
+A Fixed-Work Benchmark here describes the most intuitive approach for benchmarking: We fix a specified amount of work $W_i$ and measure the required time $T_i$ that is required to fulfil this work.
 
@@
 Additionally there are also further approaches that does not employ fixed time or work at all, but rather employ variable-time and -work characteristics.
-For this case the matric is a function of the time $T$ and the work $W$.
+For this case the metric is a function of the time $T$ and the work $W$.
 While this technique provides maximum flexibility, this approach is not suitable for all types of benchmarks (See \cite{Kounev} p.
@@
 it is not possible to create a single benchmark that covers all these attributes perfectly.
-Therefore one either has to create mutliple benchmarks that complement each others weaknesses or choose to sacrifice one of these attributes over the other (\cite{Skadron2003} p.
+Therefore one either has to create multiple benchmarks that complement each others weaknesses or choose to sacrifice one of these attributes over the other (\cite{Skadron2003} p.
 32f).
@@
 However the relevance of a benchmark may also limits the benchmarks applicability meaning, that a highly relevant benchmark for a specific system or component might only narrow applicability while benchmarks with a broad applicability will have a lower relevance but for a wider selection of applications.
-Kitowski et al.
+Kistowski et al.
 further elaborate on this with specific examples (\cite{kitowski2015} p.
@@
 
-\paragraph{Reproducibility} Reproducability ensures that it is possible for a third party to produce ideally the same results for a given test environment.
-Reproducability covers both the consistency between mutliple runs on the same system as well as creating the same results on another environment with a semantically equivalent configuration.
+\paragraph{Reproducibility} Reproducibility ensures that it is possible for a third party to produce ideally the same results for a given test environment.
+Reproducibility covers both the consistency between multiple runs on the same system as well as creating the same results on another environment with a semantically equivalent configuration.
 
-However, with modern hard- and software systems, optimal reproducability has become challenging.
+However, with modern hard- and software systems, optimal reproducibility has become challenging.
 For both hard- and software there are several factors that induce variability.
@@
 
-According to Huppler, an ideal benchmark result should be definable as a function fo a hard- and software configuration (See \cite{huppler2009} p.
+According to Huppler, an ideal benchmark result should be definable as a function of a hard- and software configuration (See \cite{huppler2009} p.
 335).
-However for real-world applications, modelling such a function is far too complex which requires the benchmark designer to try to model reproducability in other ways.
-In the end the reproducability of a benchmark is heavuly dependent on the ability to reproduce the benchamrking environment that was used to create this specific benchmark.
+However for real-world applications, modelling such a function is far too complex which requires the benchmark designer to try to model reproducibility in other ways.
+In the end the reproducibility of a benchmark is heavily dependent on the ability to reproduce the benchmarking environment that was used to create this specific benchmark.
 
@@
 	\label{ssec:bench_perf_oppo}
-	While benchmarks as a standalone tooling are alreay a useful tool to compare the performance of different systems in order to, for example, select a specific system for a given task it also offers different opportunities.
+	While benchmarks as a stand-alone tooling are already a useful tool to compare the performance of different systems in order to, for example, select a specific system for a given task it also offers different opportunities.
 One of these opportunities is to use benchmarking as a tool that is closely integrated into the development cycle in order to evaluate the systems performance throughout the development.
@@
 
-	For the first complex of the questions mentioned above, the follwoing methology is planned: Firstly, perform a benchmark of all public releases on the open-source software that was selected.
+	For the first complex of the questions mentioned above, the following methodology is planned: Firstly, perform a benchmark of all public releases on the open-source software that was selected.
 In a second step then every individual commit is benchmarked for more fine-grained data.
@@
 Lzbench is an in-memory compression benchmarking tool that is designed to compare different implementations of compression algorithms.
-For this experiment all other compression algorithm implementations will be disabled so that only \texttt{lz4} will be benachmarked at different releases and commits.
+For this experiment all other compression algorithm implementations will be disabled so that only \texttt{lz4} will be benchmarked at different releases and commits.
 
@@
 
-	Lzbench also offers a variety of command line switches that influence the behavior of the benchmark.
+	Lzbench also offers a variety of command line switches that influence the behaviour of the benchmark.
 An overview of the switches that were used for executing this experiment can be found in \autoref{tab:cmd_switches}\footnote{Also see: \url{https://github.com/inikep/lzbench}}.
@@
 The Silesia Corpus is a diverse dataset that has specifically been designed as a compression workload with the motivation in mind to include a variety of different data sources.
-By this the Silesia Corpus tries to not favor any compression algorithms that perform very well on a certain type of data(TODO: Citation needed).
+By this the Silesia Corpus tries to not favour any compression algorithms that perform very well on a certain type of data(TODO: Citation needed).
 
@@
 The results of these benchmarks will be used to identify a commit range with a significant performance change
-	\item All commits in the identified commit range will be benchmarked for a more detailed and thourough analysis.
+	\item All commits in the identified commit range will be benchmarked for a more detailed and thorough analysis.
 \end{itemize}
@@
 The benchmark itself will be performed on the Cluster Infrastructure of the Software Engineering Chair of Saarland University using Slurm\footnote{See \url{https://slurm.schedmd.com/documentation.html}}.
-The machines that are used are part of the \texttt{kine} cluster with the following hardware configuration\footnote{CPU Information has been aquired using the \texttt{lscpu} command}:
+The machines that are used are part of the \texttt{kine} cluster with the following hardware configuration\footnote{CPU Information has been acquired using the \texttt{lscpu} command}:
 

### 2021-09-22 tex/paper.tex
Continued chapter on continuous benchmarking

@@
 	\subsection{Benchmarking Before Releases}
+	\label{ssec:bench_rel}
 	The most intuitive approach to ensure the performance of a software system throughout the release history is quite simple: Based on the requirements imposed by either a customer or internal quality assurance one defines certain performance threshold that the software needs to fulfil.
@@
 If the only benchmarking data available is these from the two release candidates this results in an extensive additional overhead to retroactively reconstruct the cause of the root cause.
+Additionally when only evaluating the performance before release candidates as an affect one would also only detect a performance change at that point.
+However generally software aims to detect performance defects as soon as possible.
 
@@
 
+TODO: Elaborate how/if this can be used to compare arbitrary results
+
 	\subsection{Continuous Benchmarking}
+In this section a technique that will further be reffered to as \textit{Continuous Benchmarking} will be elaborated further.
+First the motivation of this approach will be discussed to give a working definition.
+Secondly a selection of possible continuous benchmarking strategies will be outlined.
+Lastly the possible benefits and potential challenges will be showcased and weighted to give an assessment of using such a technique.
 
 	\subsubsection{Motivation \& Definition}
+	As previously discussed in \autoref{ssec:bench_rel} benchmarking only before releases introduces several challenges.
+The general motivation of continuous benchmarking is to address these by, simply said, generally adding more data points to evaluate.
+These added data points can then be used for a more detailled analysis of the systems performance over time.
+The general idea is similar to those used in \gls{ci} and \gls{cd}.
+By running tests and releases more frequently, often after every commit, these methods aim to shorten release cycles.
+\gls{cb} however, is a term and methodology that seems not yet commonly defined in academia.
+
+	We will therefore introduce the following (working) definition for our approach to continuous benchmarking in this paper:
+	\paragraph{Continuous Benchmarking} -- A Systems Benchmarking integrated into a Continuous Integration pipeline which allows to track a (software) systems performance throughout the development process
+
 	\subsubsection{Strategies}
+	TODO: maybe remove and SPlit oppo\&Challenges into two?
+
 		\subsubsection{Opportunities and Challenges}
+
+	Tracking a software systems performance can be used in several ways. For this paper we want to focus on two points:
+	\begin{enumerate}
+		\item How can we use the performance data to detect performance changes?
+		\item Can we use this data to compare the performance of different commits?
+	\end{enumerate}
+
+	\section{Change Point Detection}
+	\subsection{Distinction from Outlier Detection}
+	\subsection{Strategies}
+	\subsubsection{Jump Detection}
+	\subsubsection{Trend Detection}
+	\subsubsection{E-Divisive Means}
 

### 2021-09-23 tex/paper.tex
Finished chapter about continuous benchmarking

@@
 \newcommand{\thetitle}{Seminar: Systems Benchmarking}
-\newcommand{\shorttitle}{Seminar: Systems Benchmarking}
+\newcommand{\shorttitle}{Systems Benchmarking}
 \newcommand{\thedate}{\today{}}
@@
 
-	\subsubsection{Motivation \& Definition}
+	\subsubsection{Definition}
 	As previously discussed in \autoref{ssec:bench_rel} benchmarking only before releases introduces several challenges.
@@
 	We will therefore introduce the following (working) definition for our approach to continuous benchmarking in this paper:
-	\paragraph{Continuous Benchmarking} -- A Systems Benchmarking integrated into a Continuous Integration pipeline which allows to track a (software) systems performance throughout the development process
+	\paragraph{Continuous Benchmarking} -- A Systems Benchmarking integrated into a Continuous Integration pipeline which allows to track a (software) systems performance throughout the development process.
 
-	\subsubsection{Strategies}
-	TODO: maybe remove and SPlit oppo\&Challenges into two?
+	\paragraph{}As for any benchmark also \gls{cb} should only be run against a correctly working software.
+Therefore if integrated into a contiuous integration pipeline, \gls{cb} should be among the last steps such that the correct functionality of the software is already ensured by the \gls{cd} tests beforehand (See \cite{grambow2019} p.
+2).
+
+	Similar to \gls{cd} approaches in \gls{cb} the question also arises when to run the \gls{cb}.
+For \gls{cd}, optimally all tests and operations should be performed after every commit.
+However in practice this might not always be feasible due to the amount of tests and the associated compute time with that which is why complex software systems often alrady use a multi-tiered approach to \gls{cb}.
+A similar question arises when deciding on when to run \gls{cb}.
+Running benchmarks after every commit can pose challenges which will be further evaulated in \autoref{sssec:cb_challenges}.
+However for this paper our main focus will not be on when to run \gls{cb} but rather how the data produced by a \gls{cb} can be used to detect performance changes.
 
@@
 
-	Tracking a software systems performance can be used in several ways. For this paper we want to focus on two points:
-	\begin{enumerate}
-		\item How can we use the performance data to detect performance changes?
-		\item Can we use this data to compare the performance of different commits?
-	\end{enumerate}
+		Using \gls{cb} opens up several opportunities for improvements to the development process of software.
+First of all it gives a regular overview of a software systems performance.
+However the usability of these results is also heavily dependent on the quality of your testbed.
+Especially the use of cloud infrastructure can introduce additional noise to the performance of a system.
+As has been shown by Daly and Ingo in \cite{daly2019} reducing the noise in such a scenario is a heavily application specific task that can take several weeks of investigating the systems behavior.
+
+	Running performance benchmarks more frequently naturally also enables to detect performance changes more quickly.
+As a result it also makes it easier to isolate the cause of the change as there may only be fa few commits between the two benchmarks.
+However again the comparability of these results heavily depends how and if we can take into account the testbeds noise accordingly as to not errornously flag outliers from noise as actual performance changes.
+In \cite{daly2021} Daly proposed a technique called \textit{canary testing} to counter these issues.
+However, in their evaluation canary testing was not viable in their productive system and resulted in more cost than benefit (See \cite{daly2021} p.
+6f).
+
+	Another point to consider when using \gls{cb} is the additional data that will inherently get produced.
+Especially for modern software systems there is not only a single benchmark that is of interest but rather multiple benchmarks with for example different system configurations or workloads.
+Therefore as Daly et al.
+and Grambow et al.
+conclude in their works that manually reviewing the performance data for \gls{cb} is not feasible(See \cite{daly2020} p.
+2, \cite{grambow2019} p.
+5).
+As a result, to assist in \gls{cb} and especially in detecting performance changes, automated approaches and toolings are required to preprocess this data and possibly detect performance changes automatically.
+Approaches for such tools have been described by Daly et al.
+(\cite{daly2020} p.
+2, \cite{daly2021} p.
+2ff) and Grambow et al.(\cite{grambow2019}).
+One of the techniques commonly referred to in this context is change point detection which will be covered in a little more detail in \autoref{sec:cp_detection}.
+
+	Lastly setting up the benchmark itself needs to be considered.
+There might not be standard tooling available for the specific software or benchmark one wants to perform, therefore additional effort may be required to build a benchmark first (See \cite{grambow2019} p.
+5).
+However the same effort has to be done when performing benchmarks manually so it is not a problem that is unique to \gls{cb}.
+What is an additional challenge for \gls{cb} however, is the increased amount of hardware and computing time required.
+In order to produce relevant results a benchmark should ideally reproduce a production-like environment.
+Therefore for complex software system an individual benchmark is considered to be run for at least 20 minutes (\cite{grambow2019} p.
+2).
+If we take into consideration the amount of commits to modern software already outlined in \autoref{ssec:bench_rel}, most likely additional infrastructure will be required if benchmarking is integrated as an automated process.
 
 	\section{Change Point Detection}
-	\subsection{Distinction from Outlier Detection}
-	\subsection{Strategies}
-	\subsubsection{Jump Detection}
-	\subsubsection{Trend Detection}
-	\subsubsection{E-Divisive Means}
+	\label{sec:cp_detection}
+	\subsection{Distinction}
+	\label{ssec:cp_distinction}
+	\subsection{E-Divisive Means}
+	\label{ssec:cp_edivisive}
 

### 2021-09-24 tex/paper.tex
Finished definition of change points and CPD

@@
 \usepackage{glossaries}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 	\label{sec:cp_detection}
-	\subsection{Distinction}
+	This chapter will give a brief introduction into a technique from signal processing known as \textit{Changepoint Detection}.
+It will briefly introduce the term Change point and it's distinction from outliers adn introduce one specific change point detection algorithm.
+
+	\subsection{Definition \& Distinction}
 	\label{ssec:cp_distinction}
+	The most commonly domain where the term "Change Point" and "Change Point Detection" are commonly used is the one of signal processing.
+Literature suggest several different definitions of what a change point is.
+According to Aminikhanghahi and Cook: "A change point represents a transition between different states in a process that generates the time series data."(\cite{Samaneh2016} p.
+4).
+It is important to understand the fundamental difference between a change point and an outlier in a time series.
+The NIST\footnote{National Institute of Standards and Technology} Engineering Statistics Handbook defines an outlier as "an observation that lies an abnormal distance from other values in a random sample from a population." (\cite{nist}, part 7.1.6).
+
+	\begin{figure}[ht!]
+		\centering
+		\begin{subfigure}[b]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{outlier}
+			\caption{Visualization of an outlier}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{changepoint}
+			\caption{Visualization of a change point}
+		\end{subfigure}
+		\caption{Visual difference of an outlier and a changepoint}
+		\label{fig:outlier_cp}
+	\end{figure}
+
+	In other words, a change point indicates that the overall underlying signal undergoes a noticable change after that point, while an outlier is only a temporary effect that generally does not persist.
+\autoref{fig:outlier_cp} shows a visualization of this distinction.
+
+	The challenge of finding such change points is commonly referred to as "Change Point Detection" and is defined by Aminikhanghahi and Cook as "the problem of finding abrupt changes in data when a property of the time series changes" (\cite{Samaneh2016}).
+In the domain of (continuous) benchmarking, change point detection can be used as a tool to determine points at which a performance regression (or improvement) occurs.
+With this regard, the performance of a system throughout different commits can be interpreted as a series of time-ordered series, which represents the underlying signal that is analyzed by a chnge-point detection algorithm (See \cite{daly2020} p.
+69)
+
 	\subsection{E-Divisive Means}

### 2021-09-26 scripts/benchmark_commits.sh
Minor changes to benchmarking scripts

@@ -13,7 +13,7 @@ USER_BASE_DIR=/scratch/$USER
 RELEASES_FILE=$USER_BASE_DIR/SystemsBenchmarking/benchmark/lz4commits
 
 RELEASES_LIST=($(<$RELEASES_FILE))
-BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/commit_benchmark
+BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/commit_benchmark/mintime
 
 PER_TASK=50
 START_NUM=$(( $SLURM_ARRAY_TASK_ID * $PER_TASK ))

### 2021-09-26 scripts/benchmark_releases.sh

@@ -13,6 +13,6 @@ RELEASES_FILE=$USER_BASE_DIR/SystemsBenchmarking/benchmark/lz4releases
 
 RELEASES_LIST=($(<$RELEASES_FILE))
 RELEASE=${RELEASES_LIST[${SLURM_ARRAY_TASK_ID}]}
-BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/release_benchmark
+BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/release_benchmark/mintime
 
 srun ./run_benchmark.sh $RELEASE $BENCH_BASE_DIR

### 2021-09-26 scripts/example.sh

@@ -2,9 +2,8 @@
 #SBATCH --job-name=testjob-luabelt
 #SBATCH --output=/scratch/abeltluk/slurm_logs/slurm_log_%j.out
 #SBATCH --time=10:00
-#SBATCH --constraint=eku
+#SBATCH --constraint=kine
 #SBATCH --partition=seminar
 
 srun sleep 10
-srun echo Hello from $(hostname)
-
+srun lscpu > /scratch/abeltluk/lscpu

### 2021-09-26 scripts/run_benchmark.sh

@@ -17,7 +17,8 @@ RESULT_FILE=$BENCH_BASE_DIR/results/$RELEASE.res
 TIMINGS_FILE=$BENCH_BASE_DIR/results/$RELEASE.timings
 
 # Setup environment
-mkdir $WORKING_DIR
+mkdir -p $WORKING_DIR
+mkdir -p $BENCH_BASE_DIR/results
 cd $WORKING_DIR
 
 # Copy LZBench and LZ4 from base
@@ -41,7 +42,7 @@ make
 
 cd $WORKING_DIR
 # Run lzbench 
-./lzbench/lzbench -elz4 -i100,100 -p3 -j -r -o4 -v silesia > $RESULT_FILE
+./lzbench/lzbench -elz4 -t60,60 -p3 -j -r -o4 -v silesia > $RESULT_FILE
 
 # Cleanup
 cd $USER_BASE_DIR

### 2021-09-26 tex/paper.tex
Finished chapter about E-Divisive means

@@
 	\label{ssec:cp_edivisive}
+	One algorithm for detecting change points is the E-Divisive Means algorithm.
+In contrast to other change point detection algorithms it offers a few benefits decribed by Daly et al.
+(See \cite{daly2020} p.
+69):
+
+	\begin{itemize}
+		\item No distributional assumptions required
+		\item Can identify multiple change points using recursion
+		\item Does noit require training data
+	\end{itemize}
+
+	The algorithm is based on hierachically dividing the given time-series into multiple clusters. The recursive approach can be summarized in three steps:
+	\begin{enumerate}
+		\item For each point in the time series calculate a statistic $\hat{Q}$
+		\item Select the largest $\hat{Q}$ as the next change point
+		\item This divides the time series into two new clusters
+	\end{enumerate}
+
+	The termination of the algorithm for a specific cluster is determined by repeating the above steps on a random permutation of the input cluster data.
+If then the highest $\hat{Q}$ value does not significantly changes it is likely that the series does not contain a relevant change point.
+
+	Within this paper the readily available python package implemented by engineers of MongoDB will be used\footnote{TODO: Link to GitHub}.
+A broad overview of the algorithm that includes the exact calculation of $\hat{Q}$ is described by the work of Daly et al.
+(\cite{daly2020} p.
+69) while an in depth description of the algorithm is given in the original paper by Matteson and James (\cite{Matteson2014}).
 
@@
 \label{sec:exp_evaluation}
+
 \section{Reflection}
 
-\section{Future Work}
+\section{Related Work}
+
+\section{Conclusion}
 

### 2021-09-27 scripts/benchmark_commits.sh
Added LZ4HC benchmarking to benchmark scripts

@@ -4,7 +4,7 @@
 #SBATCH --partition=seminar
 #SBATCH --constraint=kine
 #SBATCH --array=0-6
-#SBATCH --time=12:00:00
+#SBATCH --time=1-00:00:00
 #SBATCH --output=/scratch/abeltluk/slurm_logs/lz4commits/commit_benchmark_%A_%a.out
 #SBATCH --error=/scratch/abeltluk/slurm_logs/lz4commits/commit_benchmark_%A_%a.err
 
@@ -13,7 +13,7 @@ USER_BASE_DIR=/scratch/$USER
 RELEASES_FILE=$USER_BASE_DIR/SystemsBenchmarking/benchmark/lz4commits
 
 RELEASES_LIST=($(<$RELEASES_FILE))
-BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/commit_benchmark/mintime
+BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/commit_benchmark/lz4hc
 
 PER_TASK=50
 START_NUM=$(( $SLURM_ARRAY_TASK_ID * $PER_TASK ))

### 2021-09-27 scripts/benchmark_releases.sh

@@ -13,6 +13,6 @@ RELEASES_FILE=$USER_BASE_DIR/SystemsBenchmarking/benchmark/lz4releases
 
 RELEASES_LIST=($(<$RELEASES_FILE))
 RELEASE=${RELEASES_LIST[${SLURM_ARRAY_TASK_ID}]}
-BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/release_benchmark/mintime
+BENCH_BASE_DIR=$USER_BASE_DIR/SystemsBenchmarking/release_benchmark/lz4hc
 
 srun ./run_benchmark.sh $RELEASE $BENCH_BASE_DIR

### 2021-09-27 scripts/run_benchmark.sh

@@ -16,34 +16,65 @@ WORKING_DIR=$BENCH_BASE_DIR/build/$RELEASE
 RESULT_FILE=$BENCH_BASE_DIR/results/$RELEASE.res
 TIMINGS_FILE=$BENCH_BASE_DIR/results/$RELEASE.timings
 
+# Time start of benchmark run
+date +%s%N >> $TIMINGS_FILE
+
 # Setup environment
 mkdir -p $WORKING_DIR
 mkdir -p $BENCH_BASE_DIR/results
 cd $WORKING_DIR
 
 # Copy LZBench and LZ4 from base
+# Timing
+date +%s%N >> $TIMINGS_FILE
+
 cp -r $LZBENCH_DIR .
+
+# Timing
+date +%s%N >> $TIMINGS_FILE
+
 cp -r $LZ4_DIR .
+
+# Timing
+date +%s%N >> $TIMINGS_FILE
 
 # Copy siselia corpus
 cp -r $SILESIA_DIR .
+
+# Timing
+date +%s%N >> $TIMINGS_FILE
 
 # Checkout correct version of lz4:
 cd ./lz4
 git checkout $RELEASE
 
+# Timing
+date +%s%N >> $TIMINGS_FILE
+
 # Overwrite lz4 files of lzbench
 cd $WORKING_DIR
 cp -r ./lz4/lib/* ./lzbench/lz4
+
+# Timing
+date +%s%N >> $TIMINGS_FILE
 
 # Build lzbench with new version
 cd ./lzbench
 make
 
+# Timing
+date +%s%N >> $TIMINGS_FILE
+
 cd $WORKING_DIR
 # Run lzbench 
-./lzbench/lzbench -elz4 -t60,60 -p3 -j -r -o4 -v silesia > $RESULT_FILE
+./lzbench/lzbench -elz4/lz4hc -t60,60 -p3 -j -r -o4 -v silesia > $RESULT_FILE
+
+# Timing
+date +%s%N >> $TIMINGS_FILE
 
 # Cleanup
 cd $USER_BASE_DIR
 rm -rf $WORKING_DIR
+
+# Timing data
+date +%s%N >> $TIMINGS_FILE

### 2021-09-27 tex/paper.tex
Minor fixes for citations

@@
 Kistowski et al.
-further elaborate on this with specific examples (\cite{kitowski2015} p.
+further elaborate on this with specific examples (\cite{kistowski2015} p.
 334f)
@@
 A similar question arises when deciding on when to run \gls{cb}.
-Running benchmarks after every commit can pose challenges which will be further evaulated in \autoref{sssec:cb_challenges}.
+Running benchmarks after every commit can pose challenges which will be further evaulated in the following section.
 However for this paper our main focus will not be on when to run \gls{cb} but rather how the data produced by a \gls{cb} can be used to detect performance changes.
@@
 		\subsubsection{Opportunities and Challenges}
+		\label{sssec:cd_challenges}
 

### 2021-09-27 code/visualization/main.py
* Updated scripts to support plotting more data

@@ -7,36 +7,47 @@ import numpy.random
 
 
 def plot_release_data():
-    release_res_dir = "../../release_benchmark/mintime/results"
+    release_res_dir = "../../release_benchmark/lz4hc/results"
     labels = []
-    compression_speed = []
-    decompression_speed = []
+    compression_speed = dict()
+    decompression_speed = dict()
 
     for filename in os.listdir(release_res_dir):
+        if filename.endswith(".timings"):
+            continue
         with open(os.path.join(release_res_dir, filename)) as res_file:
             labels.append(filename.strip(".res"))
             reader = csv.reader(res_file)
+            # Skip headers and memcpy line
             next(reader)
             next(reader)
-            line = next(reader)
-            compression_speed.append(float(line[1]))
-            decompression_speed.append(float(line[2]))
+            for line in reader:
+                try:
+                    compression_speed[line[0]].append(float(line[1]))
+                    decompression_speed[line[0]].append(float(line[2]))
+                except KeyError:
+                    compression_speed[line[0]] = [float(line[1])]
+                    decompression_speed[line[0]] = [float(line[2])]
 
-    decompression_speed.sort(key=dict(zip(decompression_speed,labels)).get)
-    compression_speed.sort(key=dict(zip(compression_speed,labels)).get)
-    labels.sort()
+    plt.xticks(rotation=90)
+    sorted_labels = sorted(labels)
 
-    plt.plot(labels, decompression_speed,label="Decompression speed",color="orange")
+    for compressor in compression_speed:
+        comp_data_series = compression_speed[compressor]
+        comp_data_series.sort(key=dict(zip(comp_data_series, labels)).get)
+        plt.plot(sorted_labels, comp_data_series, label=f"Compression speed {compressor}")
+
+        # decomp_data_series = decompression_speed[compressor]
+        # decomp_data_series.sort(key=dict(zip(decomp_data_series, labels)).get)
+        # plt.plot(labels, decomp_data_series, label=f"Decompression speed {compressor}")
+
     plt.ylabel('MB/s')
     plt.xlabel("Version")
-    plt.ylim([0, 4000.0])
-    plt.xticks(rotation=90)
-
-    #plt.clf()
-    plt.plot(labels, compression_speed, label="Compression speed")
+    plt.ylim([0, 150.0])
     plt.legend()
     plt.tight_layout()
-    plt.savefig("releases_plot.png")
[…]

### 2021-09-27 tex/paper.tex
Finished chapter about experiment design

@@
 
-	\subsection{Experiment Results}
+	\subsection{Experiment Implementation and Results}
 
-\section{Evaluation of Performance Results}
+	The benchmark was implemented using a few simple bash scripts that perform an lzbench run on a given list of commits.
+The benchmark script copies all source files required for building lzbench to a separate build directory.
+It then checks out the given commit of lz4 and overwrites the lz4 specific files in the lzbench directory.
+This custom built lzbench version is then used to run the benchmark.
+All code that was used to perform this benchmark can be found on GitHub (\cite{TODO}).
+
+	\begin{figure}[ht!]
+		\centering
+		\includegraphics[width=0.8\textwidth]{outlier}
+		\caption{Compression- and Decompression speeds throughout the release history}
+		\label{fig:release-bench}
+	\end{figure}
+
+	As described in the previous section the benchmark was first performed on all versioned releases in the Git repository.
+The results of this initial run are shown in \autoref{fig:release-bench}.
+It can be observed that throughout the release history the compression speed stayed relatively consistent.
+For the decompression speed however, multiple performance increases can be observed throughout the release history.
+\autoref{tab:rel-speedup} shows the relative speedup between the individual versions.
+
+	\begin{table}
+		\caption{Relative speedup between lz4 releases}
+		\label{tab:rel-speedup}
+	\end{table}
+
+	Based on these results the commit range between \textit{v1.8.1} and \textit{v1.8.2} was selected as the commit range for a more thorough and detailled analysis.
+The results of this analysis are further discussed in \autoref{sec:exp_evaluation}.
+However as the data for the lz4 benchmark only indicated a performance improvement and the goal of this work is to evaluate the detection both performance improvements and regressions, the release benchmarks were repeated with the \texttt{lz4hc} compression algorithm.
+The \texttt{lz4hc} implementation is a variant of the \texttt{lz4} implementation that features a higher compression rate at the cost of lower compression speed.
+As \texttt{lz4hc} is also included in the same source code as \texttt{lz4} the only adaption required to the benchmark was to replace the compression algorithm used in the command line parameters passed.
+
+	\begin{figure}[ht!]
+		\centering
+		\includegraphics[width=0.8\textwidth]{outlier}
+		\caption{Compression- and Decompression speeds throughout the release history of lz4hc}
+		\label{fig:release-bench}
+	\end{figure}
+
+\section{Evaluation of Commit Benchmark Results}
 \label{sec:exp_evaluation}
@@
 \section{Reflection}
+In this section the results of this work are critically reflected upon.
+A focus is put onto the quality of the benchmark experiment ran.
+Additionally the shortcomings of the approach used will be discussed to identify potential future work that could extend this work.
+
+\subsection{Quality of the Benchmarking Experiment}
+
+\subsection{Shortcomings}
+
+\subsection{Future Work}
 

### 2021-09-27 tex/paper.tex
Minor adaptions to paper

@@
 
-In this paper we give an overview of the general concepts of system benchmarks before we consider in detail how classical benchmarking approaches can be used and extended to integrate it into the standard development process of software.
-Specifically, we take a look at how benchmark can be used to swiftly detect and react to performance changes throughout the development process.
-In order to do this we will take a look at Change-Point detection algorithms.
-We will outline and analyse the methodology and opportunities of such approaches while taking a careful look at the challenges that may arise due to this.
+This paper gives an overview of the general concepts of system benchmarks and describes how classical benchmarking approaches can be used and extended to integrate them into the standard development process of software.
+Specifically, it will outline how benchmarks can be used to swiftly detect and react to performance changes throughout the development process.
+In order to achieve this the paper will describe and use the concepts of change point detection.
+This paper will outline and analyse the methodology and opportunities of such approaches while taking a careful look at the challenges that may arise due to this.
 
-To support and evaluate our claims, we will conduct a practical experiment where we will use and compare several benchmarking techniques on a piece of well known, open-source software.
+To support and evaluate the claims, this paper includes a practical experiment that will serve as a basis to compare two benchmarking approaches on a piece of well known, open-source software.
 
@@
 The term "Benchmark" is a broad term that can be interpreted and defined in many different ways depending on the context and application domain.
-We will use this chapter to give a definition of Benchmarking how we will use it throughout this paper.
+This chapter gives a general definition of "Benchmarking" how it will use it throughout this paper.
 
@@
 While Fixed-Work benchmarks are easy to understand and implement, it introduces an implicit performance bottleneck that is also known as \textit{Amdahl's Law}.
-It states that the maximum possible performance improvement that can be achieved in Fixed-Work Benchmarks is prohibitly upper-bounded by the fraction of work that is performed by the component that is being improved (See \cite{Kounev} p.
+It states that the maximum possible performance improvement that can be achieved in Fixed-Work Benchmarks is upper-bounded by the fraction of work that is performed by the component that is being improved (See \cite{Kounev} p.
 9f).
@@
 During this period of 28 months roughly 700 commits have been added to the repository.
-Similarly for the C implementation of the LZ4 compression algorithm that can be found on GitHub\footnote{\url{https://github.com/lz4/lz4}} in the 15 months between the two most recent releases about 250 commits have been added to the code.
+Similarly for the C implementation of the \texttt{lz4} compression algorithm that can be found on GitHub\footnote{\url{https://github.com/lz4/lz4}} in the 15 months between the two most recent releases about 250 commits have been added to the code.
 
@@
 	\subsection{Continuous Benchmarking}
-In this section a technique that will further be reffered to as \textit{Continuous Benchmarking} will be elaborated further.
+In this section a technique that will further be referred to as \textit{Continuous Benchmarking} will be elaborated further.
 First the motivation of this approach will be discussed to give a working definition.
@@
 The general motivation of continuous benchmarking is to address these by, simply said, generally adding more data points to evaluate.
-These added data points can then be used for a more detailled analysis of the systems performance over time.
+These added data points can then be used for a more detailed analysis of the systems performance over time.
 The general idea is similar to those used in \gls{ci} and \gls{cd}.
@@
 	\paragraph{}As for any benchmark also \gls{cb} should only be run against a correctly working software.
-Therefore if integrated into a contiuous integration pipeline, \gls{cb} should be among the last steps such that the correct functionality of the software is already ensured by the \gls{cd} tests beforehand (See \cite{grambow2019} p.
+Therefore if integrated into a continuous integration pipeline, \gls{cb} should be among the last steps such that the correct functionality of the software is already ensured by the \gls{cd} tests beforehand (See \cite{grambow2019} p.
 2).
@@
 For \gls{cd}, optimally all tests and operations should be performed after every commit.
-However in practice this might not always be feasible due to the amount of tests and the associated compute time with that which is why complex software systems often alrady use a multi-tiered approach to \gls{cb}.
+However in practice this might not always be feasible due to the amount of tests and the associated compute time with that which is why complex software systems often already use a multi-tiered approach to \gls{cb}.
 A similar question arises when deciding on when to run \gls{cb}.
-Running benchmarks after every commit can pose challenges which will be further evaulated in the following section.
+Running benchmarks after every commit can pose challenges which will be further evaluated in the following section.
 However for this paper our main focus will not be on when to run \gls{cb} but rather how the data produced by a \gls{cb} can be used to detect performance changes.
@@
 First of all it gives a regular overview of a software systems performance.
-However the usability of these results is also heavily dependent on the quality of your testbed.
+However the usability of these results is also heavily dependent on the quality of the testbed.
 Especially the use of cloud infrastructure can introduce additional noise to the performance of a system.
@@
 As a result it also makes it easier to isolate the cause of the change as there may only be fa few commits between the two benchmarks.
-However again the comparability of these results heavily depends how and if we can take into account the testbeds noise accordingly as to not errornously flag outliers from noise as actual performance changes.
+However again the comparability of these results heavily depends how and if we can take into account the testbed's noise accordingly as to not erroneously flag outliers from noise as actual performance changes.
 In \cite{daly2021} Daly proposed a technique called \textit{canary testing} to counter these issues.
@@
 5).
-As a result, to assist in \gls{cb} and especially in detecting performance changes, automated approaches and toolings are required to preprocess this data and possibly detect performance changes automatically.
+As a result, to assist in \gls{cb} and especially in detecting performance changes, automated approaches and toolings are required to pre-process this data and possibly detect performance changes automatically.
 Approaches for such tools have been described by Daly et al.
@@
 	\label{sec:cp_detection}
-	This chapter will give a brief introduction into a technique from signal processing known as \textit{Changepoint Detection}.
-It will briefly introduce the term Change point and it's distinction from outliers adn introduce one specific change point detection algorithm.
+	This chapter will give a brief introduction into a technique from signal processing known as \textit{Change Point Detection}.
+It will briefly introduce the term Change point and it's distinction from outliers and introduce one specific change point detection algorithm.
 
@@
 		\end{subfigure}
-		\caption{Visual difference of an outlier and a changepoint}
+		\caption{Visual difference of an outlier and a change point}
 		\label{fig:outlier_cp}
@@
 
-	In other words, a change point indicates that the overall underlying signal undergoes a noticable change after that point, while an outlier is only a temporary effect that generally does not persist.
+	In other words, a change point indicates that the overall underlying signal undergoes a noticeable change after that point, while an outlier is only a temporary effect that generally does not persist.
 \autoref{fig:outlier_cp} shows a visualization of this distinction.
@@
 In the domain of (continuous) benchmarking, change point detection can be used as a tool to determine points at which a performance regression (or improvement) occurs.
-With this regard, the performance of a system throughout different commits can be interpreted as a series of time-ordered series, which represents the underlying signal that is analyzed by a chnge-point detection algorithm (See \cite{daly2020} p.
+With this regard, the performance of a system throughout different commits can be interpreted as a series of time-ordered series, which represents the underlying signal that is analyzed by a change point detection algorithm (See \cite{daly2020} p.
 69)
@@
 	One algorithm for detecting change points is the E-Divisive Means algorithm.
-In contrast to other change point detection algorithms it offers a few benefits decribed by Daly et al.
+In contrast to other change point detection algorithms it offers a few benefits described by Daly et al.
 (See \cite{daly2020} p.
@@
 		\item Can identify multiple change points using recursion
-		\item Does noit require training data
+		\item Does not require training data
 	\end{itemize}
 
-	The algorithm is based on hierachically dividing the given time-series into multiple clusters. The recursive approach can be summarized in three steps:
+	The algorithm is based on hierarchically dividing the given time-series into multiple clusters. The recursive approach can be summarized in three steps:
 	\begin{enumerate}
@@
 
-	To perform the experiment as described in \autoref{ssec:exp_goals} the open-source software LZ4\footnote{\url{https://github.com/lz4/lz4}} will be used.
-\texttt{LZ4} is a compression library with an active commit history.
-In total \texttt{LZ4} offers 31 releases and more than 2500 commits in total\footnote{As of 16.09.2021}.
+	To perform the experiment as described in \autoref{ssec:exp_goals} the open-source implementation \texttt{lz4}\footnote{\url{https://github.com/lz4/lz4}} will be used.
+\texttt{lz4} is a compression library with an active commit history.
+In total \texttt{lz4} offers 31 releases and more than 2500 commits in total\footnote{As of 16.09.2021}.
 
@@
 	Lzbench offers the option to disable all the other compression algorithms at compile time.
-The LZ4 version that is used for the benchmark can simply be changed by overwriting the corresponding lz4 files within the lzbench repository before compilation.
+The \texttt{lz4} version that is used for the benchmark can simply be changed by overwriting the corresponding lz4 files within the lzbench repository before compilation.
 In the experiment a slightly adapted version of Lzbench will be used that has the other compression algorithms disabled at compile time and also incorporates some minor changes that were required to ensure compilation on the cluster infrastructure.
@@
 
-Since the LZ4 repository consists of over 2500 commits benchmarking each individual commit is infeasible for the scope of this paper as it would both generate too much data to evaluate properly as well as strain the available shared server resources too much.
+	Since the \texttt{lz4} repository consists of over 2500 commits benchmarking each individual commit is infeasible for the scope of this paper as it would both generate too much data to evaluate properly as well as strain the available shared server resources too much.
 Therefore a two staged approach will be used:
@@
 
-The benchmark itself will be performed on the Cluster Infrastructure of the Software Engineering Chair of Saarland University using Slurm\footnote{See \url{https://slurm.schedmd.com/documentation.html}}.
+The benchmark itself will be performed on the cluster infrastructure of the Software Engineering Chair of Saarland University using Slurm\footnote{See \url{https://slurm.schedmd.com/documentation.html}}.
 The machines that are used are part of the \texttt{kine} cluster with the following hardware configuration\footnote{CPU Information has been acquired using the \texttt{lscpu} command}:
@@
 
-	Based on these results the commit range between \textit{v1.8.1} and \textit{v1.8.2} was selected as the commit range for a more thorough and detailled analysis.
+	Based on these results the commit range between \textit{v1.8.1} and \textit{v1.8.2} was selected as the commit range for a more thorough and detailed analysis.
 The results of this analysis are further discussed in \autoref{sec:exp_evaluation}.

### 2021-09-28 tex/paper.tex
Added information about further structure of paper

@@
 				\item Reducing the amount of manual work required by the developer?
-				\item Can we use this metric to compare arbitrary commits?
+				\item Can we use this metric to compare arbitrary commits? TODO: Maybe remove
 			\end{itemize}
@@
 
+	Based on these results, it can be seen that there is a significant performance regression between versions \textit{v1.8.0} and \textit{v1.8.1}.
+Therefore this commit range was also selected for further investigation of the individual commits.
+
 \section{Evaluation of Commit Benchmark Results}
 \label{sec:exp_evaluation}
+
+\subsection{Reviewing the Performance Benchmark Data}
+-Baseline: E-Divisive Means
+-Mention Performance Spike
+
+\subsection{Comparing Methods to Detect Performance Changes}
+-E-Divisive Means
+-Jump Detection
+-Trend Detection
+
+Swiftness of detection w/ all three
+
+\subsection{Conclusion}
+benefits/problems of each detection method
 

### 2021-09-28 code/PythonProcessing/data_import.py
* Slightly restructured project

@@ -1,0 +1,30 @@
+def import_benchmark_data(commit_file, result_directory):
+    commit_res_dir = "../../commit_benchmark/lz4hc_180_181/results"
+    commit_hash_file = "../../benchmark/lz4hc_commits"
+
+    compression_speed = dict()
+    decompression_speed = dict()
+    labels = []
+
+    with open(commit_hash_file) as hash_file:
+        for commit_hash in hash_file:
+            # Check if a res file exists for this commit
+            if not os.path.isfile(os.path.join(commit_res_dir, commit_hash.strip() + ".res")):
+                continue
+            with open(os.path.join(commit_res_dir, commit_hash.strip() + ".res")) as commit_file:
+                reader = csv.reader(commit_file)
+                labels.append(commit_hash)
+                # Skip first 2 lines (Header and memcpy lines)
+                next(reader)
+                next(reader)
+
+                for line in reader:
+                    try:
+                        compression_speed[line[0]].append(float(line[1]))
+                        decompression_speed[line[0]].append(float(line[2]))
+                    except KeyError:
+                        compression_speed[line[0]] = [float(line[1])]
+                        decompression_speed[line[0]] = [float(line[2])]
+            # print(commit_hash.strip()+".res")
+
+    return compression_speed, decompression_speed, labels

### 2021-09-28 code/PythonProcessing/main.py

@@ -1,0 +1,6 @@
+from visualization import plot_commit_data
+
+if __name__ == '__main__':
+    plot_commit_data()
+
+# See PyCharm help at https://www.jetbrains.com/help/pycharm/

### 2021-09-28 code/PythonProcessing/visualization.py

@@ -1,0 +1,128 @@
+import csv
+import os
+
+import matplotlib.pyplot as plt
+from signal_processing_algorithms.energy_statistics import energy_statistics
+import numpy.random
+
+
+def plot_release_data():
+    release_res_dir = "../../release_benchmark/lz4hc/results"
+    labels = []
+    compression_speed = dict()
+    decompression_speed = dict()
+
+    for filename in os.listdir(release_res_dir):
+        if filename.endswith(".timings"):
+            continue
+        with open(os.path.join(release_res_dir, filename)) as res_file:
+            labels.append(filename.strip(".res"))
+            reader = csv.reader(res_file)
+            # Skip headers and memcpy line
+            next(reader)
+            next(reader)
+            for line in reader:
+                try:
+                    compression_speed[line[0]].append(float(line[1]))
+                    decompression_speed[line[0]].append(float(line[2]))
+                except KeyError:
+                    compression_speed[line[0]] = [float(line[1])]
+                    decompression_speed[line[0]] = [float(line[2])]
+
+    plt.xticks(rotation=90)
+    sorted_labels = sorted(labels)
+
+    for compressor in compression_speed:
+        #Only temporary to only show lz4hc
+        #compressor = "lz4hc 1.9.2 -1"
+
+        comp_data_series = compression_speed[compressor]
+        comp_data_series.sort(key=dict(zip(comp_data_series, labels)).get)
+        plt.plot(sorted_labels, comp_data_series, label=f"Compression speed (lz4hc)")
+
+        decomp_data_series = decompression_speed[compressor]
+        decomp_data_series.sort(key=dict(zip(decomp_data_series, labels)).get)
+        plt.plot(sorted_labels, decomp_data_series, label=f"Decompression speed (lz4hc)",color="orange")
+        #break
+
+    plt.ylabel('MB/s')
+    plt.xlabel("Version")
+    plt.ylim([0, 4000.0])
+    plt.legend()
+    plt.tight_layout()
+    #plt.show()
+    plt.savefig("out/lz4hc_release_decompression.png")
+
+
+def plot_commit_data():
+    commit_res_dir = "../../commit_benchmark/lz4hc_180_181/results"
+    commit_hash_file = "../../benchmark/lz4hc_commits"
+    compression_speed = []
[…]

### 2021-09-28 code/visualization/main.py

@@ -1,127 +1,0 @@
-import csv
-import os
-
-import matplotlib.pyplot as plt
-from signal_processing_algorithms.energy_statistics import energy_statistics
-import numpy.random
-
-
-def plot_release_data():
-    release_res_dir = "../../release_benchmark/lz4hc/results"
-    labels = []
-    compression_speed = dict()
-    decompression_speed = dict()
-
-    for filename in os.listdir(release_res_dir):
-        if filename.endswith(".timings"):
-            continue
-        with open(os.path.join(release_res_dir, filename)) as res_file:
-            labels.append(filename.strip(".res"))
-            reader = csv.reader(res_file)
-            # Skip headers and memcpy line
-            next(reader)
-            next(reader)
-            for line in reader:
-                try:
-                    compression_speed[line[0]].append(float(line[1]))
-                    decompression_speed[line[0]].append(float(line[2]))
-                except KeyError:
-                    compression_speed[line[0]] = [float(line[1])]
-                    decompression_speed[line[0]] = [float(line[2])]
-
-    plt.xticks(rotation=90)
-    sorted_labels = sorted(labels)
-
-    for compressor in compression_speed:
-        comp_data_series = compression_speed[compressor]
-        comp_data_series.sort(key=dict(zip(comp_data_series, labels)).get)
-        plt.plot(sorted_labels, comp_data_series, label=f"Compression speed {compressor}")
-
-        # decomp_data_series = decompression_speed[compressor]
-        # decomp_data_series.sort(key=dict(zip(decomp_data_series, labels)).get)
-        # plt.plot(labels, decomp_data_series, label=f"Decompression speed {compressor}")
-
-    plt.ylabel('MB/s')
-    plt.xlabel("Version")
-    plt.ylim([0, 150.0])
-    plt.legend()
-    plt.tight_layout()
-    #plt.show()
-    plt.savefig("test.png")
-
-
-def plot_commit_data():
-    commit_res_dir = "../../commit_benchmark/mintime/results/"
-    commit_hash_file = "../../benchmark/merge_commits"
-    compression_speed = []
-    decompression_speed = []
-    labels = []
-
-    with open(commit_hash_file) as hash_file:
-        for commit_hash in hash_file:
-            if not os.path.isfile(os.path.join(commit_res_dir,commit_hash.strip()+".res")):
[…]

### 2021-09-28 code/PythonProcessing/data_import.py
* Finished dividing of visualization and data import

@@ -1,17 +1,19 @@
+import csv
+import os
+
 def import_benchmark_data(commit_file, result_directory):
-    commit_res_dir = "../../commit_benchmark/lz4hc_180_181/results"
-    commit_hash_file = "../../benchmark/lz4hc_commits"
 
     compression_speed = dict()
     decompression_speed = dict()
     labels = []
 
-    with open(commit_hash_file) as hash_file:
+    with open(commit_file) as hash_file:
         for commit_hash in hash_file:
             # Check if a res file exists for this commit
-            if not os.path.isfile(os.path.join(commit_res_dir, commit_hash.strip() + ".res")):
+            if not os.path.isfile(os.path.join(result_directory, commit_hash.strip() + ".res")):
                 continue
-            with open(os.path.join(commit_res_dir, commit_hash.strip() + ".res")) as commit_file:
+
+            with open(os.path.join(result_directory, commit_hash.strip() + ".res")) as commit_file:
                 reader = csv.reader(commit_file)
                 labels.append(commit_hash)
                 # Skip first 2 lines (Header and memcpy lines)

### 2021-09-28 code/PythonProcessing/main.py

@@ -1,6 +1,6 @@
-from visualization import plot_commit_data
+from visualization import *
 
 if __name__ == '__main__':
-    plot_commit_data()
+    plot_release_data()
 
 # See PyCharm help at https://www.jetbrains.com/help/pycharm/

### 2021-09-28 code/PythonProcessing/visualization.py

@@ -1,6 +1,8 @@
 import csv
 import os
 
+from data_import import import_benchmark_data
+
 import matplotlib.pyplot as plt
 from signal_processing_algorithms.energy_statistics import energy_statistics
 import numpy.random
@@ -8,26 +10,9 @@ import numpy.random
 
 def plot_release_data():
     release_res_dir = "../../release_benchmark/lz4hc/results"
-    labels = []
-    compression_speed = dict()
-    decompression_speed = dict()
+    release_list_file = "../../benchmark/lz4releases"
 
-    for filename in os.listdir(release_res_dir):
-        if filename.endswith(".timings"):
-            continue
-        with open(os.path.join(release_res_dir, filename)) as res_file:
-            labels.append(filename.strip(".res"))
-            reader = csv.reader(res_file)
-            # Skip headers and memcpy line
-            next(reader)
-            next(reader)
-            for line in reader:
-                try:
-                    compression_speed[line[0]].append(float(line[1]))
-                    decompression_speed[line[0]].append(float(line[2]))
-                except KeyError:
-                    compression_speed[line[0]] = [float(line[1])]
-                    decompression_speed[line[0]] = [float(line[2])]
+    compression_speed, decompression_speed, labels = import_benchmark_data(release_list_file,release_res_dir,)
 
     plt.xticks(rotation=90)
     sorted_labels = sorted(labels)
@@ -50,36 +35,22 @@ def plot_release_data():
     plt.ylim([0, 4000.0])
     plt.legend()
     plt.tight_layout()
-    #plt.show()
-    plt.savefig("out/lz4hc_release_decompression.png")
+    plt.show()
+    #plt.savefig("out/lz4hc_release_decompression.png")
 
 
 def plot_commit_data():
     commit_res_dir = "../../commit_benchmark/lz4hc_180_181/results"
     commit_hash_file = "../../benchmark/lz4hc_commits"
-    compression_speed = []
-    decompression_speed = []
-    labels = []
-
-    # with open(commit_hash_file) as hash_file:
-    #     for commit_hash in hash_file:
-    #         if not os.path.isfile(os.path.join(commit_res_dir,commit_hash.strip()+".res")):
-    #             continue
-    #         with open(os.path.join(commit_res_dir,commit_hash.strip()+".res")) as commit_file:
-    #             reader = csv.reader(commit_file)
[…]

### 2021-09-28 tex/paper.tex
* Added data analysis python code * Minor additions to paper

@@
 			\centering
-			\includegraphics[width=\textwidth]{outlier}
+			\includegraphics[width=\textwidth]{graph/outlier}
 			\caption{Visualization of an outlier}
@@
 			\centering
-			\includegraphics[width=\textwidth]{changepoint}
+			\includegraphics[width=\textwidth]{graph/changepoint}
 			\caption{Visualization of a change point}
@@
 		\centering
-		\includegraphics[width=0.8\textwidth]{outlier}
+		\includegraphics[width=0.8\textwidth]{graph/lz4_releases_plot}
 		\caption{Compression- and Decompression speeds throughout the release history}
@@
 		\centering
-		\includegraphics[width=0.8\textwidth]{outlier}
-		\caption{Compression- and Decompression speeds throughout the release history of lz4hc}
-		\label{fig:release-bench}
+		\begin{subfigure}[b]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{graph/lz4hc_release_compression}
+			\caption{Compression speed of \texttt{lz4hc} releases}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{graph/lz4hc_release_decompression}
+			\caption{Decompression speed of \texttt{lz4hc} releases}
+		\end{subfigure}
+		\caption{Compression and Decompression speeds of \texttt{lz4hc} releases}
+		\label{fig:release-bench-lz4hc}
 	\end{figure}
 
-	Based on these results, it can be seen that there is a significant performance regression between versions \textit{v1.8.0} and \textit{v1.8.1}.
+	While the graph for the decompression speed is similar to the one for the normal \texttt{lz4} algorithm, for the compression speed a significant performance regression can be observed between versions \textit{v1.8.0} and \textit{v1.8.1}.
 Therefore this commit range was also selected for further investigation of the individual commits.

### 2021-09-28 code/PythonProcessing/data_analysis.py

@@ -1,0 +1,56 @@
+from statistics import mean
+
+from signal_processing_algorithms.energy_statistics import energy_statistics
+
+
+def jump_detection(time_series, relative_threshold = 0.05):
+    jump_points = []
+
+    idx=1
+    last_point = time_series[0]
+
+    for current_point in time_series[1:]:
+        relative_change = abs((current_point/last_point)-1)
+
+        if relative_change > relative_threshold:
+            jump_points.append(idx)
+
+        idx+=1
+        last_point = current_point
+
+    return jump_points
+
+def trend_detection(time_series, window_length,threshhold):
+    jump_points = []
+
+    idx = window_length
+    while idx < len(time_series):
+        moving_average = mean(time_series[idx-window_length:idx-1])
+
+        relative_change = abs((time_series[idx] / moving_average) - 1)
+
+        if relative_change > threshhold:
+            jump_points.append(idx)
+
+        idx+=1
+
+    return jump_points
+
+def e_divisive_analysis(time_series):
+    change_points = energy_statistics.e_divisive(time_series, pvalue=0.1, permutations=100)
+    if len(change_points) == 0:
+        return dict()
+
+    result = dict()
+
+    for idx in range(1,len(time_series)):
+        partial_changepoints = energy_statistics.e_divisive(time_series[:idx], pvalue=0.1, permutations=100)
+
+        for cp in change_points:
+            if cp in result:
+                continue
+
+            if cp in partial_changepoints:
+                result[cp] = idx
+
+    return result

### 2021-09-28 code/PythonProcessing/main.py

@@ -1,6 +1,35 @@
 from visualization import *
+from data_import import *
+from data_analysis import *
 
 if __name__ == '__main__':
-    plot_release_data()
+    commit_res_dir = "../../commit_benchmark/lz4hc_180_181/results"
+    commit_hash_file = "../../benchmark/lz4hc_commits"
+
+    comp_dict, decomp_dict, labels = import_benchmark_data(commit_hash_file, commit_res_dir)
+
+    compression_speed = comp_dict["lz4hc 1.9.2 -1"]
+    decompression_speed = decomp_dict["lz4hc 1.9.2 -1"]
+
+    comp_jd = jump_detection(compression_speed)
+    decomp_jd = jump_detection(decompression_speed)
+
+    print("Jump detection points")
+    print(comp_jd)
+    print(decomp_jd)
+
+    comp_trend = trend_detection(compression_speed,10,0.05)
+    decomp_trend = trend_detection(decompression_speed,10,0.05)
+
+    print("Trend detection points")
+    print(comp_trend)
+    print(decomp_trend)
+
+    comp_analysis = e_divisive_analysis(compression_speed)
+    decomp_analysis = e_divisive_analysis(decompression_speed)
+
+    print("E_Divisive Analysis")
+    print(comp_analysis)
+    print(decomp_analysis)
 
 # See PyCharm help at https://www.jetbrains.com/help/pycharm/

### 2021-09-28 tex/paper.tex
Continued on paper

@@
 \subsection{Evaluating Benchmarks}
-
+\label{ssec:eval_bm}
 Apart from the metrics that evaluate the result of a benchmark, there are also several attributes that are important to evaluate the quality of the benchmark itself.
@@
 \label{sec:exp_evaluation}
+This chapter will cover a more thorough analysis of the performance benchmark performed on the identified commit ranges in the previous chapter.
+Specifically it will compare three algorithms that can be used to detect performance changes and tries to evaluate them.
 
 \subsection{Reviewing the Performance Benchmark Data}
--Baseline: E-Divisive Means
--Mention Performance Spike
+Before applying automated analysis methods to the data gathered, a manual evaluation of the data gathered from the performance benchmark was conducted.
+The data gathered for the decompression speed from the \texttt{lz4} benchmark is shown in \autoref{fig:lz4_commit_bench}, while the compression speed data gathered from from the \texttt{lz4hc} benchmark can be seen in \autoref{fig:lz4hc_commit_bench}.
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{graph/lz4_commits_decompression}
+	\caption{Decompression speed of \texttt{lz4} between releases \textit{v1.8.1} and \textit{v1.8.2}}
+	\label{fig:lz4_commit_bench}
+\end{figure}
+
+For the analysis of \texttt{lz4} data there are a few key observation that we made while evaluating the data manually.
+First of all, it seems that there are at least two general "performance levels" that can be observed from the data: While the majority of the data lies around a speed of 2200 MB/s in the end we see a clear improvement to a level of around 2400 MB/s.
+We also see that at the very beginning and near the end two more steep increases can be oberseved.
+However as we are missing the data before and after these benchmarks we cannot rule them out to just be outliers in the dataset.
+Therefore we do not consider these as additional performance levels.
+
+Another observation that we made were the intense performance increases that can be observed throughout the data series that peak to around 2900 MB/s.
+While manually reviewing the code changes in the corresponding code commits we could not find any connection to the code changes made that would cause such a spike in the decompression speed nor did we find any evidence of changes being reverted in the following commits that would cause the performance to return to the previous level.
+This observation will be further discussed in \autoref{ssec:refl_quality} and \autoref{ssec:refl_shortcomings}.
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{graph/lz4hc_commits_compression}
+	\caption{Decompression speed of \texttt{lz4hc} between releases \textit{v1.8.0} and \textit{v1.8.1}}
+	\label{fig:lz4hc_commit_bench}
+\end{figure}
+
+For the data observed for the \texttt{lz4hc} benchmark the data observed does not draw such a clear picture as for the \texttt{lz4} one.
+From our perspective only one clear change point can be directly observed for the performance drop near the end.
+Before that there is a lot of fluctuation in the data.
+One can observe a few short plateaus emerging in the performance data before that, however we cannot decide if these are just effects of random noise or actual relevant performance changes.
 
 \subsection{Comparing Methods to Detect Performance Changes}
--E-Divisive Means
--Jump Detection
--Trend Detection
+After manually reviewing the data we performed a programmatic evaluation of the data with three different methods.
+Apart from the E-Divisive means algorithm that was already discussed in \autoref{ssec:cp_edivisive}, we will use two more algorithms that were also evaluated by Grambow et al.
+(See \cite{grambow2019}):
 
-Swiftness of detection w/ all three
+\paragraph{Jump Detection}: This approach performs a relative comparison of the benchmarking data from the current commit to the one right before it.
+If they diverge by more than a defined percentage, the performance change will be flagged.
+In our evaluation we used a threshold of 5\%.
+
+\paragraph{Trend Detection}: For trend detection we do not compare the current data to the value of the previous commit but rather we compare it to a moving average of the last $b$ commits.
+Then similarly to jump detection we check the relative change to this and flag this.
+For our evaluation we used $b=10$ and similar to jump detection a threshold of 5\%.
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c||c|c|c|}
+		\hline
+		\textbf{Benchmark}&\textbf{Jump Detection}&\textbf{Trend Detection}&\textbf{E-Divisive Means}
+		\\\hline\hline
+		\texttt{lz4}&24&27&4
+		\\\hline
+		\texttt{lz4hc}&23&43&3
+		\\\hline
+	\end{tabular}
+	\caption{Overview of changes detected by the different methods}
+\end{table}
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c||c|c|c|}
+		\hline
+		\textbf{Benchmark}&\textbf{Jump Detection}&\textbf{Trend Detection}&\textbf{E-Divisive Means}
+		\\\hline\hline
+		\texttt{lz4}&24&27&4
+		\\\hline
+		\texttt{lz4hc}&23&43&3
+		\\\hline
+	\end{tabular}
+	\caption{Overview of changes detected by the different methods}
+\end{table}
+After applying these techniques we observed that they differ vastly in the amount of supposed performance changes that they detect.
+In \autoref{tab:perf_changes} we list how many performance changes were detected for each technique, while \autoref{fig:perf_commit_cp} shows a visual representation of the change points in the datasets.
+
+\begin{figure}[ht!]
+	\centering
+	\begin{subfigure}[b]{0.3\textwidth}
+		\includegraphics[width=\textwidth]{graph/lz4_commit_e-divisive}
+		\caption{\texttt{lz4} using E-Divisive Means}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.3\textwidth}
+		\includegraphics[width=\textwidth]{graph/lz4_commit_jump}
+		\caption{\texttt{lz4} using Jump Detection}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.3\textwidth}
+		\includegraphics[width=\textwidth]{graph/lz4_commit_trend}
+		\caption{\texttt{lz4} using Trend Detection}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.3\textwidth}
+		\includegraphics[width=\textwidth]{graph/lz4hc_commit_e-divisive}
+		\caption{\texttt{lz4hc} using E-Divisive Means}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.3\textwidth}
+		\includegraphics[width=\textwidth]{graph/lz4hc_commit_jump}
+		\caption{\texttt{lz4hc} using Jump Detection}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.3\textwidth}
+		\includegraphics[width=\textwidth]{graph/lz4hc_commit_trend}
+		\caption{\texttt{lz4hc} using Trend Detection}
+	\end{subfigure}
+	\caption{Graphical representation of all change detections on the both datasets}
+	\label{fig:}
+\end{figure}
+
+Surprisingly for us, for both datasets the trend detection flagged the most commits as a performance change.
+We initially expected that because of the many outliers in our dataset that jump detection would flag the most commits as for every outlier two commits would be flagged -- the outlier and the commit right after that.
+By far the fewest commits were flagged as changes buy the E-Divisive Means algorithm.
+To our surprise E-Divisive for the \texttt{lz4} algorithm flagged two additional change points with a relatively small overall performance change that we missed in our manual review.
+While it is impressive that E-Divisive Mean can detect such changes it is a matter of application domain whether detecting such changes is desirable or if further parameters of the algorithm needs to be tuned.
+
+One more aspect we wanted to evaluate was how quickly these techniques can be detect a performance change after it has occured.
+While our experiment retroactively looks for change points, we are more interested how and if such techniques can be used to find performance changes while they are introduced.
+
+Intuitively by the nature of Jump Detection it can detect a performance change immediately after it occurs.
+For trend detection a change can be observed anywhere within the moving average that is given and therefore the detection time depends on the defined parameters.
+
+As E-Divisive means is a different and much more sophisticated change point detection algorithm as the other two evaluating when a change will be detected is not as trivial.
+However as E-Divisive means specifically only detects change points and not outliers, it will never flag the latest commit as a performance change as this could very well be the result of an outlier.
+
+To evaluate how quickly a performance change is detected by E-Divisive Means, we use the data we gather to retroactively "simulate" an ongoing continuous benchmarking approach.
+That is we iteratively add one commit by one to the time series and therefore find the first occurence of the change points identified in our final time series.
+The results of this evaluation are shown in \autoref{tab:ediv_occ}
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c||c|c|c|}
+		\hline
+		\textbf{Dataset}&\textbf{Change Point Commit\#}&\textbf{First detected at Commit \#}&\textbf{$\Delta$}
+		\\\hline\hline
+		\texttt{lz4}&3&7&4
+		\\\hline
+		\texttt{lz4}&52&64&12
+		\\\hline
+		\texttt{lz4}&251&287&31
+		\\\hline
+		\texttt{lz4}&313&316&6
+		\\\hline
+		\texttt{lz4hc}&36&37&1
+		\\\hline
+		\texttt{lz4hc}&104&122&18
+		\\\hline
+		\texttt{lz4hc}&122&123&1
+		\\\hline
+	\end{tabular}
+	\caption{Overview of changes detected by the different methods}
+\end{table}
+
+So for our example, E-Divisive Means detects the changes relatively quich in most cases.
+When reviewing these commits by hand we found that the biggest time difference was about four weeks until the change point got detected (Between commit 104 and 122 for \texttt{lz4hc}).
+For most of the other change points it was only a few days until the detection.
+Whether or not a detection time of four weeks is acceptable is heavily project dependent and cannot be answered by us generically.
 
 \subsection{Conclusion}
-benefits/problems of each detection method
+We believe that all three algorithms presented in this chapter offer useful properties for certain application with respect to detecting performance changes.
+However when it comes to reliably detecting performance changes throughout the development, we believe that E-Divisive Means stands out against the other two.
+Jump Detection is neturally prone to noisy signals while for trend detection we observed a fairly poor performance on bi-modal data as we partly oberseved it in our \texttt{lz4} dataset.
+
+However also E-Divisive means has its drawbacks that should be considered before implementing it: For a reliable and vast change detection one needs to regularly benchmark the \gls{sut}, optimally after every code change.
+In practice this might not be viable.
+Also we observed that it flags even smaller performance changes which might not desirable.
+Lastly depending on the performance data it might take some time for the algorithm to identify a change point.
+However for this last point one needs to consider that E-Divisive Means still identifies the exact point where a performance change was introduced which potentially reduces the amount to find the corresponding code change by far.
 
@@
 	\subsection{Quality of the Benchmarking Experiment}
+	\label{ssec:refl_quality}
+	In this chapter we will focus on the quality of our benchmarking experiment we conducted.
+We will hereby evaluate each of the five quality attributes that were already mentioned in \autoref{ssec:eval_bm}.
+
+	\paragraph{Relevance} -- We believe that this aspect has to be viewed from two different angles.
+The first one would be, how relevant the benchmark is in terms of detecting performance changes in the \texttt{lz4} software.
+In this regard we believe that this benchmark certainly provides a specific relevance as we have shown with different techniques how to retroactively identify performance changes in the software.
+
+	The other aspect however, is how relevant the results of our experiment are to our overarching question: "Should we benchmark software only before releases or after every commit".
+For this we believe our benchmark has only a limited relevance.
+The main reason for this is that our experiment only covered a really simplified and streamlined example.
+For the example of \texttt{lz4} performing a benchmark after every commit might be feasible; However our benchmark did not at all consider the dimension of modern software systems such as configurability which makes this approach unfeasible for most potential use-cases.
+
+\paragraph{Reproducibility} -- As all code artifact that have been used to perform this benchmark have been documented in a GitHub repository.
+A third-party could use these in addition to the information given in this paper regrding the hardware configuration to closely reproduce the results.
+
+\paragraph{Fairness} -- As for fairness there are a few things to critisize.
+Our benchmark is completely created artificially and is overly simplistic by nature.
+Therefore the fairness of our benchmarking approach could be questionable.
+
+\paragraph{Verifiability} -- In terms of verifiability, our benchmark ensures that only a predefined software configuration is used.
+However our benchmark only copies the build files from an existing directory on the users hardware and does not validade if any unexpected changes have been made.
+In an extended approach we would rather consider the code to be cloned directly from a public Git repository, preferably with a specific commit defined.
+
+Additionally our detailled experiment contained some outliers that we could not explain based on our findings.
+We now believe that this might be an error in our benchmarking approach as firstly, the achieved performance results are closely to those from recent \texttt{lz4} versions.
+Additionally when repeating the benchmark on a smaller subset, we could not reliably reproduce these results.
+Unfortunately in the timeframe of this seminar we could not identify the exact cause of this.
+
+\paragraph{Usability} -- In terms of usability, we believe that our benchmark is, at most to a certain extent, quite usable.
+While we used a compute cluster to run multiple benchmarks in parallel we believe that comparable results could also be reproduced by just using one local machine.
 
 	\subsection{Shortcomings}
+	\label{ssec:refl_shortcomings}
+	Question not fully answered
+	Problems in experiment setup
+	Not usable for complex software systems
+	Applicability in practice of E-Divisive
 

### 2021-09-29 tex/paper.tex
Finished content of the paper

@@
 	\label{ssec:refl_shortcomings}
-	Question not fully answered
-	Problems in experiment setup
-	Not usable for complex software systems
-	Applicability in practice of E-Divisive
+	There are several shortcomings of our experiment that can be discussed.
+First of all we have already discussed that there were some inconsistencies in the data gathered from the experiment.
+This has caused some, otherwise unexplainable, performance spikes in the data.
+As we could not reliably reproduce this behavior we believe that there is some issue in our benchmarking pipeline which leads to a wrong version of \texttt{lz4} being used.
+Therefore, one could argue that it cannot be out ruled that also other data recorded is not flawed in some other unnoticed way.
+
+	Secondly while we have retroactively identified change points using our methodology we have not performed any verification on these.
+Optimally we should have verified if the change points we identified are actually related to code changes by manually reviewing the corresponding commits in the Git history.
+This was not done in the scope of this paper due to the limited time available.
+
+	Thirdly our benchmark experiment itself was too simplistic in nature.
+It gives a broad first overview however we believe that it is generally not transferable to the development of complex software systems.
 
@@
 
+	To react and further evaluate on the shortcomings identified there are several opportunities for future works that could extend this paper.
+Most significantly we should focus on fixing the benchmark suite itself such that we can verify the correctness of the data produced.
+
+	Secondly we believe that for future works the focus of the research question should shift a bit.
+While this work shows that in an optimal scenario one should benchmark every commit, this is not applicable in practive.
+Therefore the focus should rather shift to find strategies to preemptively select the "correct" commits for benchmarking.
+
+	Lastly we believe that that aspect of configurability needs to be further considered.
+While we already collected data for two variants of \texttt{lz4}, we did not use it yet to find any collaborations between the data.
+We believe that exploring possibilities to link performance changes across variants can be very benefitial.
+
 \section{Related Work}
 
+Several similar work has been published regarding continuous performance benchmarking.
+Both Antz et al.
+and Waller at al.
+describe methods how benchmarking can be included into a continuous integration pipeline to enable continuous benchmarking(\cite{}).
+Additionally Daly desribes in multiple works how a continuous benchmarking approach has been introduced to MongoDB to enable better detection of performance changes.
+
+In the domain of identifying performance changes across different software configurations and variants, Apel et al.
+present a novel change point detection algorithm that can identify configuration-dependent performance changes while only exploring a small subset of the configuration space (\cite{}).
+
+Multiple works have also been presented to predict performance changes in software based in order to reduce the amount of commits that need to be benchmarked.
+One of these approaches is \textit{Perphecy} presented by Oliveria et al.
+(\cite{}).
+Similarly, Chen et al.
+present an approach which identifies which predicts which test cases may suffer from performance regressions after a code change(\cite{}).
+
 \section{Conclusion}
+
+In this paper we tried to answer the question whether one should benchmark software only before releases or after every commit.
+We have explored both possibilities and compared different performance change detection methods.
+We come to the conclusion that, in an optimal scenario, benchmarking every commit would be the preferrable option.
+
+However we also want to highlight that this paper is based on data from a overly simplistic benchmark and suffers from several shortcomings.
+Therefore the applicability to productive systems is limited and for most real world systems benchmarking every commit is simply not feasible.
+
+We therefore highlight that further work is required to sufficiently answer the question.
+Most notably it needs to be explored in which ways the overall number of commits and configurations to benchmark can be reduced while still reliably detecting performance changes.
 

### 2021-09-29 tex/paper.tex
Finished paper content

@@
 "a standard tool for competitive evaluation and comparison of competitive systems" (\cite{kistowski2015} p.
-X).
+333).
 
@@
 security, system reliability and energy efficiency, modern benchmarks also try to cover much more aspects of a software.
-We will discuss a selection of the quality attributes listed by Kounev et al.
-that are usually target of modern benchmarks(\cite{Kounev} p.
+According to Kounev et al.
+quality metrics of modern benchmarks are usually(\cite{Kounev} p.
 6 f):
+\begin{itemize}
+	\item Performance
+	\item Scalability
+	\item	Energy Efficiency
+	\item Reliability
+\end{itemize}
 
-\paragraph{Performance} The term Performance itself can be interpreted in many different means.
+%\paragraph{Performance} The term Performance itself can be interpreted in many different means.
 For this paper, we will focus on one of the most basic interpretations: The amount of work done compared to the time and resources used.
@@
 
-\paragraph{Scalability} TODO Definition needed
+%\paragraph{Scalability} TODO Definition needed
 
-\paragraph{Energy Efficiency} TODO Definition needed
+%\paragraph{Energy Efficiency} TODO Definition needed
 
-\paragraph{Reliability} TODO Definition needed
+%\paragraph{Reliability} TODO Definition needed
 
-When it comes to benchmarking strategies two approaches are most prominent: Fixed-Time and Fixed-Work benchmarks.
+In terms of benchmarking strategies three general approaches can be distinguished:
+\begin{enumerate}
+	\item Fixed-Time Benchmarks
+	\item Fixed-Work Benchmarks
+	\item Variable Time- and Work-Benchmarks
+\end{enumerate}
+
+All of these offer there own benefits, drawbacks and specific use-cases. These are discussed in detail by Kounev et al.(\cite{Kounev} p. 9ff)
+
+%When it comes to benchmarking strategies two approaches are most prominent: Fixed-Time and Fixed-Work benchmarks.
 A Fixed-Work Benchmark here describes the most intuitive approach for benchmarking: We fix a specified amount of work $W_i$ and measure the required time $T_i$ that is required to fulfil this work.
 
-While Fixed-Work benchmarks are easy to understand and implement, it introduces an implicit performance bottleneck that is also known as \textit{Amdahl's Law}.
+%While Fixed-Work benchmarks are easy to understand and implement, it introduces an implicit performance bottleneck that is also known as \textit{Amdahl's Law}.
 It states that the maximum possible performance improvement that can be achieved in Fixed-Work Benchmarks is upper-bounded by the fraction of work that is performed by the component that is being improved (See \cite{Kounev} p.
@@
 
-In Fixed-Time benchmarks, instead of fixing the amount of work $W_i$, the time $T_i$ is bound and the amount of work finished in this time is measured as a metric.
+%In Fixed-Time benchmarks, instead of fixing the amount of work $W_i$, the time $T_i$ is bound and the amount of work finished in this time is measured as a metric.
 As opposed to Fixed-Work Benchmarks the Fixed-Time Benchmarks do not suffer the issue of an upper-bounded maximum improvement as for every improvement, the reduced time can be used to process further work units (See \cite{Kounev} p.
@@
 
-Additionally there are also further approaches that does not employ fixed time or work at all, but rather employ variable-time and -work characteristics.
+%Additionally there are also further approaches that does not employ fixed time or work at all, but rather employ variable-time and -work characteristics.
 For this case the metric is a function of the time $T$ and the work $W$.
@@
 Kounev at al.
-list five core criteria that will be defined in a little more detail in this chapter (\cite{Kounev} p.
+list five core criteria that are generally of interest(\cite{Kounev} p.
 13f).
@@
 (See \cite{kistowski2015})
-
-\paragraph{Relevance} For a benchmark to be meaningful it is important that it, at least to a certain extent, reproduces some scenarios with real world application.
+\begin{itemize}
+	\item Relevance
+	\item Reproducibility
+	\item Fairness
+	\item Verifiability
+	\item Usability
+\end{itemize}
+%\paragraph{Relevance} For a benchmark to be meaningful it is important that it, at least to a certain extent, reproduces some scenarios with real world application.
 This is what the "Relevance" of a benchmark refers to.
@@
 
-\paragraph{Reproducibility} Reproducibility ensures that it is possible for a third party to produce ideally the same results for a given test environment.
+%\paragraph{Reproducibility} Reproducibility ensures that it is possible for a third party to produce ideally the same results for a given test environment.
 Reproducibility covers both the consistency between multiple runs on the same system as well as creating the same results on another environment with a semantically equivalent configuration.
 
-However, with modern hard- and software systems, optimal reproducibility has become challenging.
+%However, with modern hard- and software systems, optimal reproducibility has become challenging.
 For both hard- and software there are several factors that induce variability.
@@
 
-According to Huppler, an ideal benchmark result should be definable as a function of a hard- and software configuration (See \cite{huppler2009} p.
+%According to Huppler, an ideal benchmark result should be definable as a function of a hard- and software configuration (See \cite{huppler2009} p.
 335).
@@
 
-\paragraph{Fairness} TODO: Short explanation
-\paragraph{Verifiability} TODO: Short explanation
-\paragraph{Usability} TODO: Short explanation
+%\paragraph{Fairness} TODO: Short explanation
+%\paragraph{Verifiability} TODO: Short explanation
+%\paragraph{Usability} TODO: Short explanation
 
@@
 As an example one can take a look at a few open-source repositories.
-The C++ test framework \textit{googletest}\footnote{See \url{https://github.com/google/googletest}} by Google with it's most recent release (\textit{1.11.0}) in June 2021, while the last release before that (\textit{1.10.0}) was released in October 2019.
+The C++ test framework \textit{googletest} (\cite{gtest}) by Google with it's most recent release (\textit{1.11.0}) in June 2021, while the last release before that (\textit{1.10.0}) was released in October 2019.
 During this period of 28 months roughly 700 commits have been added to the repository.
-Similarly for the C implementation of the \texttt{lz4} compression algorithm that can be found on GitHub\footnote{\url{https://github.com/lz4/lz4}} in the 15 months between the two most recent releases about 250 commits have been added to the code.
+Similarly for the C implementation of the \texttt{lz4} compression algorithm that can be found on GitHub (\cite{gitlz4}) in the 15 months between the two most recent releases about 250 commits have been added to the code.
 
@@
 1).
-
-TODO: Elaborate how/if this can be used to compare arbitrary results
 
@@
 
-	Within this paper the readily available python package implemented by engineers of MongoDB will be used\footnote{TODO: Link to GitHub}.
+	Within this paper the readily available python package implemented by engineers of MongoDB will be used(\cite{gitmongo}).
 A broad overview of the algorithm that includes the exact calculation of $\hat{Q}$ is described by the work of Daly et al.
 (\cite{daly2020} p.
-69) while an in depth description of the algorithm is given in the original paper by Matteson and James (\cite{Matteson2014}).
+69) while an in depth description of the algorithm is given in the original paper by Matteson and James (\cite{Matteson2013}).
 
@@
 				\item Reducing the amount of manual work required by the developer?
-				\item Can we use this metric to compare arbitrary commits? TODO: Maybe remove
 			\end{itemize}
@@
 
-	To perform the experiment as described in \autoref{ssec:exp_goals} the open-source implementation \texttt{lz4}\footnote{\url{https://github.com/lz4/lz4}} will be used.
+	To perform the experiment as described in \autoref{ssec:exp_goals} the open-source implementation \texttt{lz4}(\cite{gitlz4}) will be used.
 \texttt{lz4} is a compression library with an active commit history.
@@
 
-	For the benchmark itself the open source project \texttt{lzbench}\footnote{\url{https://github.com/inikep/lzbench}} will be used.
+	For the benchmark itself the open source project \texttt{lzbench}(\cite{gitlzbench}) will be used.
 Lzbench is an in-memory compression benchmarking tool that is designed to compare different implementations of compression algorithms.
@@
 	Lzbench also offers a variety of command line switches that influence the behaviour of the benchmark.
-An overview of the switches that were used for executing this experiment can be found in \autoref{tab:cmd_switches}\footnote{Also see: \url{https://github.com/inikep/lzbench}}.
+An overview of the switches that were used for executing this experiment can be found in \autoref{tab:cmd_switches}.
 
 	\begin{table}
-		\caption{Overview of used command line switches for lzbench}
+		\caption{Overview of used command line switches for lzbench (\cite{gitlzbench})}
 		\label{tab:cmd_switches}
@@
 
-	As a workload for the compression benchmark the Silesia Data Corpus will be used\footnote{\url{http://sun.aei.polsl.pl/~sdeor/index.php?page=silesia}}.
+	As a workload for the compression benchmark the Silesia Data Corpus will be used.
 The Silesia Corpus is a diverse dataset that has specifically been designed as a compression workload with the motivation in mind to include a variety of different data sources.
-By this the Silesia Corpus tries to not favour any compression algorithms that perform very well on a certain type of data(TODO: Citation needed).
+By this the Silesia Corpus tries to not favour any compression algorithms that perform very well on a certain type of data(\cite{silesia}).
 
@@
 This custom built lzbench version is then used to run the benchmark.
-All code that was used to perform this benchmark can be found on GitHub (\cite{TODO}).
+All code that was used to perform this benchmark can be found on GitHub (\cite{gitSysBench}).
 
@@
 For the decompression speed however, multiple performance increases can be observed throughout the release history.
-\autoref{tab:rel-speedup} shows the relative speedup between the individual versions.
-
-	\begin{table}
-		\caption{Relative speedup between lz4 releases}
-		\label{tab:rel-speedup}
-	\end{table}
 
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{graph/lz4_commits_decompression}
-	\caption{Decompression speed of \texttt{lz4} between releases \textit{v1.8.1} and \textit{v1.8.2}}
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=\textwidth]{graph/lz4_commits_decompression}
+		\caption{Decompression speed of \texttt{lz4}}
 		\label{fig:lz4_commit_bench}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=\textwidth]{graph/lz4hc_commits_compression}
+		\caption{Decompression speed of \texttt{lz4hc}}
+		\label{fig:lz4hc_commit_bench}
+	\end{subfigure}
+	\caption{Benchmark results for individual commits}
 \end{figure}
@@
 This observation will be further discussed in \autoref{ssec:refl_quality} and \autoref{ssec:refl_shortcomings}.
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=0.8\textwidth]{graph/lz4hc_commits_compression}
-	\caption{Decompression speed of \texttt{lz4hc} between releases \textit{v1.8.0} and \textit{v1.8.1}}
-	\label{fig:lz4hc_commit_bench}
-\end{figure}
 
@@
 	\caption{Overview of changes detected by the different methods}
-\end{table}
-
-\begin{table}
-	\centering
-	\begin{tabular}{|c||c|c|c|}
-		\hline
-		\textbf{Benchmark}&\textbf{Jump Detection}&\textbf{Trend Detection}&\textbf{E-Divisive Means}
-		\\\hline\hline
-		\texttt{lz4}&24&27&4
-		\\\hline
-		\texttt{lz4hc}&23&43&3
-		\\\hline
-	\end{tabular}
-	\caption{Overview of changes detected by the different methods}
+	\label{tab:perf_changes}
 \end{table}
@@
 	\caption{Graphical representation of all change detections on the both datasets}
-	\label{fig:}
+	\label{fig:perf_commit_cp}
 \end{figure}
@@
 	\caption{Overview of changes detected by the different methods}
+	\label{tab:ediv_occ}
 \end{table}
@@
 \paragraph{Reproducibility} -- As all code artifact that have been used to perform this benchmark have been documented in a GitHub repository.
-A third-party could use these in addition to the information given in this paper regrding the hardware configuration to closely reproduce the results.
+A third-party could use these in addition to the information given in this paper regarding the hardware configuration to closely reproduce the results.
 
-\paragraph{Fairness} -- As for fairness there are a few things to critisize.
+\paragraph{Fairness} -- As for fairness there are a few things to criticise.
 Our benchmark is completely created artificially and is overly simplistic by nature.
@@
 \paragraph{Verifiability} -- In terms of verifiability, our benchmark ensures that only a predefined software configuration is used.
-However our benchmark only copies the build files from an existing directory on the users hardware and does not validade if any unexpected changes have been made.
+However our benchmark only copies the build files from an existing directory on the users hardware and does not validate if any unexpected changes have been made.
 In an extended approach we would rather consider the code to be cloned directly from a public Git repository, preferably with a specific commit defined.
 
-Additionally our detailled experiment contained some outliers that we could not explain based on our findings.
+Additionally our detailed experiment contained some outliers that we could not explain based on our findings.
 We now believe that this might be an error in our benchmarking approach as firstly, the achieved performance results are closely to those from recent \texttt{lz4} versions.
 Additionally when repeating the benchmark on a smaller subset, we could not reliably reproduce these results.
-Unfortunately in the timeframe of this seminar we could not identify the exact cause of this.
+Unfortunately in the time frame of this seminar we could not identify the exact cause of this.
 
@@
 	Secondly we believe that for future works the focus of the research question should shift a bit.
-While this work shows that in an optimal scenario one should benchmark every commit, this is not applicable in practive.
+While this work shows that in an optimal scenario one should benchmark every commit, this is not applicable in practice.
 Therefore the focus should rather shift to find strategies to preemptively select the "correct" commits for benchmarking.
@@
 While we already collected data for two variants of \texttt{lz4}, we did not use it yet to find any collaborations between the data.
-We believe that exploring possibilities to link performance changes across variants can be very benefitial.
+We believe that exploring possibilities to link performance changes across variants can be very beneficial.
 
@@
 and Waller at al.
-describe methods how benchmarking can be included into a continuous integration pipeline to enable continuous benchmarking(\cite{}).
-Additionally Daly desribes in multiple works how a continuous benchmarking approach has been introduced to MongoDB to enable better detection of performance changes.
+describe methods how benchmarking can be included into a continuous integration pipeline to enable continuous benchmarking(\cite{antz2019}, \cite{waller2015}).
+Additionally Daly describes in multiple works how a continuous benchmarking approach has been introduced to MongoDB to enable better detection of performance changes(\cite{daly2020}, \cite{daly2021}).
 
 In the domain of identifying performance changes across different software configurations and variants, Apel et al.
-present a novel change point detection algorithm that can identify configuration-dependent performance changes while only exploring a small subset of the configuration space (\cite{}).
+present a novel change point detection algorithm that can identify configuration-dependent performance changes while only exploring a small subset of the configuration space (\cite{apel2020}).
 
@@
 One of these approaches is \textit{Perphecy} presented by Oliveria et al.
-(\cite{}).
+(\cite{oliveira2017}).
 Similarly, Chen et al.
-present an approach which identifies which predicts which test cases may suffer from performance regressions after a code change(\cite{}).
+present an approach which identifies which predicts which test cases may suffer from performance regressions after a code change(\cite{chen2020}).
 
@@
 We have explored both possibilities and compared different performance change detection methods.
-We come to the conclusion that, in an optimal scenario, benchmarking every commit would be the preferrable option.
+We come to the conclusion that, in an optimal scenario, benchmarking every commit would be the preferable option.
 

### 2021-09-29 tex/paper.tex
Minor changes and corrections to paper

@@
 \label{ssec:bench_definition}
-The term "Benchmark" is used in a variety of different domains and, according to the Standard Specialization Evaluation Corporation, historically stems from a physical marking that was used as a reference point on a workbench to check the length of the produced pieces\footnote{SPEC Glossary: \url{https://www.spec.org/spec/glossary/\#benchmark}}.
+According to the Standard Specialization Evaluation Corporation, historically the term "Benchmark" stems from a physical marking that was used as a reference point on a workbench to check the length of the produced pieces\footnote{SPEC Glossary: \url{https://www.spec.org/spec/glossary/\#benchmark}}.
 However throughout this paper we are only interested in system benchmarks within the context of software systems and will therefore also refer to the definition of a benchmark as given by Kounev et al.: "a tool coupled with a methodology for the evaluation and comparison of systems or components with respect to specific characteristics, such as performance, reliability or security." (\cite{Kounev} p.
@@
 The main motivation of competitive benchmarks is hereby the development of standardized quality criteria that can be used to compare different systems.
-Certain sources also emphasize this importance on the competitiveness by providing a more detailed definition of the term benchmark, i.e.
-"a standard tool for competitive evaluation and comparison of competitive systems" (\cite{kistowski2015} p.
-333).
 
@@
 Research benchmarks on the other hand commonly refer to tools and workloads that may be used for in-depth evaluation of research results, prototypes or productive systems.
-Based on these descriptions it becomes apparent that there sometimes might be no clear distinction between a rating tool and a research benchmark and the terminology is often determined by the evaluating party (See \cite{Kounev} p.
+Based on these descriptions it becomes apparent that there sometimes is no clear distinction between a rating tool and a research benchmark and the terminology is often determined by the evaluating party (See \cite{Kounev} p.
 4).
 
-Regardless of the competitiveness, or lack thereof, of a benchmark the key metrics that are evaluated are often similar or even identical.
+Regardless of the competitiveness, or lack thereof, of a benchmark the key metrics that are evaluated are often similar.
 While historically the main metrics of importance were e.g.
@@
 13f).
-A much more in depth discussion of these criteria was performed by Kistowski et al.
+A more in depth definition and discussion of these criteria was performed by Kistowski et al.
 (See \cite{kistowski2015})
@@
 
-	As a result if not including any performance evaluation might lead to performance regressions being shipped in a stable release to customers and users.
+	As a result not including any performance evaluation might lead to performance regressions being shipped in a stable release to customers and users.
 Therefore using benchmarks throughout the development process can ensure to detect performance changes and allows to fix them before they are being released (See \cite{daly2021} p.
@@
 	Additionally employing benchmark on a regular basis also opens the window of opportunity for many other improvements if the corresponding infrastructure is setup accordingly.
-Daly describes in great detail how this was achieved for the MongoDB infrastructure in \cite{daly2021}.
+Daly describes in great detail how this was achieved for the MongoDB infrastructure (\cite{daly2021}).
 In summary the following have been observed:
@@
 a new \textit{Release Candidate} is created internally, the development team can use this benchmark to evaluate whether the candidate introduces a performance regression or if it is fit for a release.
-There are several benefits of this approach; First of all, it does not necessarily requires an automated performance testing infrastructure but rather can be executed and evaluated manually be the development team.
+There are several benefits of this approach; First of all, it does not necessarily requires an automated performance testing infrastructure but rather can be executed and evaluated manually by the development team.
 
@@
 2).
-If the only benchmarking data available is these from the two release candidates this results in an extensive additional overhead to retroactively reconstruct the cause of the root cause.
+If the only benchmarking data available is these from the two release candidates this results in an extensive additional overhead to retroactively reconstruct the cause of the regression.
 Additionally when only evaluating the performance before release candidates as an affect one would also only detect a performance change at that point.
@@
 	\subsubsection{Definition}
-	As previously discussed in \autoref{ssec:bench_rel} benchmarking only before releases introduces several challenges.
-The general motivation of continuous benchmarking is to address these by, simply said, generally adding more data points to evaluate.
+	As previously discussed in \autoref{ssec:bench_rel}, benchmarking only before releases introduces several challenges.
+The general motivation of continuous benchmarking is to address these by, simply said, generating more data points to evaluate.
 These added data points can then be used for a more detailed analysis of the systems performance over time.
@@
 Especially the use of cloud infrastructure can introduce additional noise to the performance of a system.
-As has been shown by Daly and Ingo in \cite{daly2019} reducing the noise in such a scenario is a heavily application specific task that can take several weeks of investigating the systems behavior.
+As has been shown by Daly and Ingo (\cite{daly2019}) reducing the noise in such a scenario is a heavily application specific task that can take several weeks of investigating the systems behavior.
 
 	Running performance benchmarks more frequently naturally also enables to detect performance changes more quickly.
-As a result it also makes it easier to isolate the cause of the change as there may only be fa few commits between the two benchmarks.
+As a result it also makes it easier to isolate the cause of the change as there may only be a few commits between the two benchmarks.
 However again the comparability of these results heavily depends how and if we can take into account the testbed's noise accordingly as to not erroneously flag outliers from noise as actual performance changes.
-In \cite{daly2021} Daly proposed a technique called \textit{canary testing} to counter these issues.
+Daly proposed a technique called \textit{canary testing} to counter these issues.
 However, in their evaluation canary testing was not viable in their productive system and resulted in more cost than benefit (See \cite{daly2021} p.
@@
 2ff) and Grambow et al.(\cite{grambow2019}).
-One of the techniques commonly referred to in this context is change point detection which will be covered in a little more detail in \autoref{sec:cp_detection}.
+One of the techniques commonly referred to in this context is change point detection which will be covered in more detail in \autoref{sec:cp_detection}.
 
@@
 	\label{ssec:cp_distinction}
-	The most commonly domain where the term "Change Point" and "Change Point Detection" are commonly used is the one of signal processing.
+	The domain where the terms "Change Point" and "Change Point Detection" are commonly used is the one of signal processing.
 Literature suggest several different definitions of what a change point is.
@@
 
-	The main idea of the experiment that was created was to perform a benchmark on a series of versions of a specific open-source software to evaluate the methods and techniques described in this paper.
+	The main idea of the experiment performed was to perform a benchmark on a series of versions of a specific open-source software to evaluate the methods and techniques described in this paper.
 More specifically, we want to evaluate the following questions:
@@
 
-	Additionally the experiment should also be used to identify other, currently unidentified, challenges and opportunities that this approach might offer.
+	Additionally the experiment should also be used to identify other, currently unidentified, challenges and opportunities that this approach might pose.
 
-	For the first complex of the questions mentioned above, the following methodology is planned: Firstly, perform a benchmark of all public releases on the open-source software that was selected.
+	For the first complex of the questions mentioned above, the following methodology is planned: First, perform a benchmark of all public releases on the open-source software that was selected.
 In a second step then every individual commit is benchmarked for more fine-grained data.
@@
 	For the benchmark itself the open source project \texttt{lzbench}(\cite{gitlzbench}) will be used.
-Lzbench is an in-memory compression benchmarking tool that is designed to compare different implementations of compression algorithms.
+\texttt{Lzbench} is an in-memory compression benchmarking tool that is designed to compare different implementations of compression algorithms.
 For this experiment all other compression algorithm implementations will be disabled so that only \texttt{lz4} will be benchmarked at different releases and commits.
 
-	Lzbench offers the option to disable all the other compression algorithms at compile time.
-The \texttt{lz4} version that is used for the benchmark can simply be changed by overwriting the corresponding lz4 files within the lzbench repository before compilation.
+	\texttt{Lzbench} offers the option to disable all the other compression algorithms at compile time.
+The \texttt{lz4} version that is used for the benchmark can simply be changed by overwriting the corresponding \texttt{lz4} files within the \texttt{lzbench} repository before compilation.
 In the experiment a slightly adapted version of Lzbench will be used that has the other compression algorithms disabled at compile time and also incorporates some minor changes that were required to ensure compilation on the cluster infrastructure.
 
-	Lzbench also offers a variety of command line switches that influence the behaviour of the benchmark.
+	\texttt{Lzbench} also offers a variety of command line switches that influence the behaviour of the benchmark.
 An overview of the switches that were used for executing this experiment can be found in \autoref{tab:cmd_switches}.
@@
 			\hline
-			\texttt{-i100,100} & Sets the minimum number of compression and decompression iterations to $100$ \\
+			\texttt{-t60,60} & Sets the minimum time for compression and decompression to $60$ seconds \\
 			\hline
@@
 The results of these benchmarks will be used to identify a commit range with a significant performance change
-	\item All commits in the identified commit range will be benchmarked for a more detailed and thorough analysis.
+	\item All commits in the identified commit range will be benchmarked for a more detailed analysis.
 \end{itemize}
@@
 
-	The benchmark was implemented using a few simple bash scripts that perform an lzbench run on a given list of commits.
-The benchmark script copies all source files required for building lzbench to a separate build directory.
-It then checks out the given commit of lz4 and overwrites the lz4 specific files in the lzbench directory.
-This custom built lzbench version is then used to run the benchmark.
+	The benchmark was implemented using a few simple bash scripts that performs an \texttt{lzbench} run on a given list of commits.
+The benchmark script copies all source files required for building \texttt{lzbench} to a separate build directory.
+It then checks out the given commit of lz4 and overwrites the \texttt{lz4} specific files in the \texttt{lzbench} directory.
+This custom built \texttt{lzbench} version is then used to run the benchmark.
 All code that was used to perform this benchmark can be found on GitHub (\cite{gitSysBench}).
@@
 		\includegraphics[width=0.8\textwidth]{graph/lz4_releases_plot}
-		\caption{Compression- and Decompression speeds throughout the release history}
+		\caption{Compression- and Decompression speeds of throughout the release history}
 		\label{fig:release-bench}
@@
 For the decompression speed however, multiple performance increases can be observed throughout the release history.
-
-	Based on these results the commit range between \textit{v1.8.1} and \textit{v1.8.2} was selected as the commit range for a more thorough and detailed analysis.
-The results of this analysis are further discussed in \autoref{sec:exp_evaluation}.
-However as the data for the lz4 benchmark only indicated a performance improvement and the goal of this work is to evaluate the detection both performance improvements and regressions, the release benchmarks were repeated with the \texttt{lz4hc} compression algorithm.
-The \texttt{lz4hc} implementation is a variant of the \texttt{lz4} implementation that features a higher compression rate at the cost of lower compression speed.
-As \texttt{lz4hc} is also included in the same source code as \texttt{lz4} the only adaption required to the benchmark was to replace the compression algorithm used in the command line parameters passed.
 
@@
 
+	Based on these results the commit range between \textit{v1.8.1} and \textit{v1.8.2} was selected as the commit range for a more thorough and detailed analysis.
+The results of this analysis are further discussed in \autoref{sec:exp_evaluation}.
+However as the data for the \texttt{lz4} benchmark only indicated a performance improvement and the goal of this work is to evaluate the detection both performance improvements and regressions, the release benchmarks were repeated with the \texttt{lz4hc} compression algorithm.
+The \texttt{lz4hc} implementation is a variant of the \texttt{lz4} implementation that features a higher compression rate at the cost of lower compression speed.
+As \texttt{lz4hc} is also included in the same source code as \texttt{lz4} the only adaption required to the benchmark was to replace the compression algorithm used in the command line parameters passed.
+
+	The results of this analysis are shown in \autoref{fig:release-bench-lz4hc}.
 While the graph for the decompression speed is similar to the one for the normal \texttt{lz4} algorithm, for the compression speed a significant performance regression can be observed between versions \textit{v1.8.0} and \textit{v1.8.1}.
@@
 First of all, it seems that there are at least two general "performance levels" that can be observed from the data: While the majority of the data lies around a speed of 2200 MB/s in the end we see a clear improvement to a level of around 2400 MB/s.
-We also see that at the very beginning and near the end two more steep increases can be oberseved.
+We also see that at the very beginning and near the end two more steep increases can be observed.
 However as we are missing the data before and after these benchmarks we cannot rule them out to just be outliers in the dataset.
@@
 
-Another observation that we made were the intense performance increases that can be observed throughout the data series that peak to around 2900 MB/s.
+Another observation that we made were the abrupt performance increases that can be observed throughout the data series that peak to around 2900 MB/s.
 While manually reviewing the code changes in the corresponding code commits we could not find any connection to the code changes made that would cause such a spike in the decompression speed nor did we find any evidence of changes being reverted in the following commits that would cause the performance to return to the previous level.
@@
 Apart from the E-Divisive means algorithm that was already discussed in \autoref{ssec:cp_edivisive}, we will use two more algorithms that were also evaluated by Grambow et al.
-(See \cite{grambow2019}):
+(See \cite{grambow2019} p.
+3):
 
@@
 Surprisingly for us, for both datasets the trend detection flagged the most commits as a performance change.
-We initially expected that because of the many outliers in our dataset that jump detection would flag the most commits as for every outlier two commits would be flagged -- the outlier and the commit right after that.
+We initially expected, because of the many outliers in our dataset, that jump detection would flag the most commits as for every outlier two commits would be flagged -- the outlier and the commit right after that.
 By far the fewest commits were flagged as changes buy the E-Divisive Means algorithm.
 To our surprise E-Divisive for the \texttt{lz4} algorithm flagged two additional change points with a relatively small overall performance change that we missed in our manual review.
-While it is impressive that E-Divisive Mean can detect such changes it is a matter of application domain whether detecting such changes is desirable or if further parameters of the algorithm needs to be tuned.
+While it is interesting that E-Divisive Mean can detect such changes it is a matter of application domain whether detecting such changes is desirable or if further parameters of the algorithm needs to be tuned.
 
-One more aspect we wanted to evaluate was how quickly these techniques can be detect a performance change after it has occured.
+One more aspect we wanted to evaluate was how quickly these techniques can detect a performance change after it has occurred.
 While our experiment retroactively looks for change points, we are more interested how and if such techniques can be used to find performance changes while they are introduced.
@@
 
-To evaluate how quickly a performance change is detected by E-Divisive Means, we use the data we gather to retroactively "simulate" an ongoing continuous benchmarking approach.
-That is we iteratively add one commit by one to the time series and therefore find the first occurence of the change points identified in our final time series.
+To evaluate how quickly a performance change is detected by E-Divisive Means, we use the data we gathered to retroactively "simulate" an ongoing continuous benchmarking approach.
+That is we iteratively add one commit by one to the time series and find the first occurrence of the change points identified in our final time series.
 The results of this evaluation are shown in \autoref{tab:ediv_occ}
@@
 
-So for our example, E-Divisive Means detects the changes relatively quich in most cases.
+For our example, E-Divisive Means detects the changes relatively quick in most cases.
 When reviewing these commits by hand we found that the biggest time difference was about four weeks until the change point got detected (Between commit 104 and 122 for \texttt{lz4hc}).
@@
 However when it comes to reliably detecting performance changes throughout the development, we believe that E-Divisive Means stands out against the other two.
-Jump Detection is neturally prone to noisy signals while for trend detection we observed a fairly poor performance on bi-modal data as we partly oberseved it in our \texttt{lz4} dataset.
+Jump Detection is naturally prone to noisy signals while for trend detection we observed a fairly poor performance on bi-modal data as we partly observed it in our \texttt{lz4} dataset.
 
@@
 Lastly depending on the performance data it might take some time for the algorithm to identify a change point.
-However for this last point one needs to consider that E-Divisive Means still identifies the exact point where a performance change was introduced which potentially reduces the amount to find the corresponding code change by far.
+However for this last point one needs to consider that E-Divisive Means still identifies the exact point where a performance change was introduced which potentially reduces the amount to find the corresponding code change.
 
@@
 However our benchmark only copies the build files from an existing directory on the users hardware and does not validate if any unexpected changes have been made.
-In an extended approach we would rather consider the code to be cloned directly from a public Git repository, preferably with a specific commit defined.
+In an extended approach we would rather consider the code to be cloned directly from the public Git repository, preferably with a specific commit defined.
 
 Additionally our detailed experiment contained some outliers that we could not explain based on our findings.
-We now believe that this might be an error in our benchmarking approach as firstly, the achieved performance results are closely to those from recent \texttt{lz4} versions.
+We now believe that this might be an error in our benchmarking approach as the achieved performance results are closely to those from recent \texttt{lz4} versions.
 Additionally when repeating the benchmark on a smaller subset, we could not reliably reproduce these results.
@@
 As we could not reliably reproduce this behavior we believe that there is some issue in our benchmarking pipeline which leads to a wrong version of \texttt{lz4} being used.
-Therefore, one could argue that it cannot be out ruled that also other data recorded is not flawed in some other unnoticed way.
+Therefore, one could argue that it cannot be ruled out that also other data recorded is not flawed in some other unnoticed way.
 

### 2021-09-29 code/PythonProcessing/data_analysis.py
* Minor improvements for pyhton scripts

@@ -44,6 +44,7 @@ def e_divisive_analysis(time_series):
     result = dict()
 
     for idx in range(1,len(time_series)):
+        print(idx)
         partial_changepoints = energy_statistics.e_divisive(time_series[:idx], pvalue=0.1, permutations=100)
 
         for cp in change_points:

### 2021-09-29 code/PythonProcessing/main.py

@@ -3,27 +3,20 @@ from data_import import *
 from data_analysis import *
 
 if __name__ == '__main__':
-    commit_res_dir = "../../commit_benchmark/lz4hc_180_181/results"
-    commit_hash_file = "../../benchmark/lz4hc_commits"
+    # plot_commits_with_cp()
+
+    commit_res_dir = "../../commit_benchmark/lz4hc/results"
+    commit_hash_file = "../../benchmark/lz4commits"
 
     comp_dict, decomp_dict, labels = import_benchmark_data(commit_hash_file, commit_res_dir)
 
-    compression_speed = comp_dict["lz4hc 1.9.2 -1"]
-    decompression_speed = decomp_dict["lz4hc 1.9.2 -1"]
+    compression_speed = comp_dict["lz4 1.9.2"]
+    decompression_speed = decomp_dict["lz4 1.9.2"]
 
-    comp_jd = jump_detection(compression_speed)
-    decomp_jd = jump_detection(decompression_speed)
+    compression_speed.reverse()
+    decompression_speed.reverse()
 
-    print("Jump detection points")
-    print(comp_jd)
-    print(decomp_jd)
-
-    comp_trend = trend_detection(compression_speed,10,0.05)
-    decomp_trend = trend_detection(decompression_speed,10,0.05)
-
-    print("Trend detection points")
-    print(comp_trend)
-    print(decomp_trend)
+    print("Starting Analysis")
 
     comp_analysis = e_divisive_analysis(compression_speed)
     decomp_analysis = e_divisive_analysis(decompression_speed)

### 2021-09-29 code/PythonProcessing/visualization.py

@@ -1,6 +1,7 @@
 import csv
 import os
 
+from data_analysis import jump_detection, trend_detection
 from data_import import import_benchmark_data
 
 import matplotlib.pyplot as plt
@@ -40,20 +41,20 @@ def plot_release_data():
 
 
 def plot_commit_data():
-    commit_res_dir = "../../commit_benchmark/lz4hc_180_181/results"
-    commit_hash_file = "../../benchmark/lz4hc_commits"
+    commit_res_dir = "../../commit_benchmark/lz4hc/results"
+    commit_hash_file = "../../benchmark/lz4commits"
 
     comp_dict, decomp_dict, labels = import_benchmark_data(commit_hash_file,commit_res_dir)
-
-    compression_speed = comp_dict["lz4hc 1.9.2 -1"]
-    decompression_speed = decomp_dict["lz4hc 1.9.2 -1"]
+    print(decomp_dict)
+    compression_speed = comp_dict["lz4 1.9.2"]
+    decompression_speed = decomp_dict["lz4 1.9.2"]
 
     decompression_speed.reverse()
     compression_speed.reverse()
-    plt.plot(compression_speed, label="Compression Speed (lz4hc)")
-    plt.plot(decompression_speed, label="Decompression Speed (lz4hc)", color="orange")
+    #plt.plot(compression_speed, label="Compression Speed (lz4hc)")
+    plt.plot(decompression_speed, label="Decompression Speed", color="orange")
     plt.ylabel('MB/s')
-    plt.xlabel("# of commits since v1.8.0")
+    plt.xlabel("# of commits since v1.8.1")
     plt.ylim([0,4000])
     plt.legend(loc=9)
 
@@ -75,9 +76,76 @@ def plot_commit_data():
     plt.tight_layout()
     labels.reverse()
     # print(labels[decompression_speed.index(max(decompression_speed))])
-    plt.show()
+    # plt.show()
 
-    # plt.savefig("out/lz4hc_commits_decompression")
+    plt.savefig("out/lz_commits_decompression")
+
+
+def plot_commits_with_cp():
+    plt.figure(dpi=600)
+    commit_res_dir = "../../commit_benchmark/lz4hc_180_181/results"
+    commit_hash_file = "../../benchmark/lz4hc_commits"
+
+    comp_dict, decomp_dict, labels = import_benchmark_data(commit_hash_file, commit_res_dir)
+    print(decomp_dict)
[…]
